---
title: "mapping"
output: html_document
---

# Install and load packages:
```{r}
rm(list = ls())
pacman::p_load(
  tidyverse,
  ggplot2,
  here,
  stringr,
  paletteer,
  readr,
  dplyr,
  forcats,
  scales,
  treemapify,
  rphylopic,
  RColorBrewer,
  viridis,
  tidyr,
  forcats,
  bibliometrix,
  scales,
  treemap,
  ComplexUpset, # for upset plot
  patchwork,
  wordcloud2,
  textstem,
  SnowballC,
  sf,
  rnaturalearthdata,
  rnaturalearth,
  ggalluvial,
  circlize,
  countrycode
)


```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Load data
```{r}
#Load data
map <- read_csv(here("Data", "Dataset1_map_data_extraction.csv"))
biblio <- read_csv(here("Data", "Dataset2_bibliometric_data.csv"))
bib_data <- convert2df(here("Data", "bibliometric.bib"), dbsource = "scopus", format = "bibtex")
dat_policy <- read.csv(here("Data", "Dataset_3_policy_data_extraction.csv"))
pol_ci <- read_csv(here("Data", "Dataset_3.1_policy_citation_counts_PlumX.csv"))
dat_ceesat <- read.csv(here("Data", "Dataset5_ceesat_processed.csv"))
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure 1: Systematic map 

## Panel A: Quantitative and qualitative studies counts

```{r}
# 1. Process the quantitative/qualitative column
quant_type <- map %>%
  select(study_id, year, quantitative) %>%
  mutate(quant = case_when(
    tolower(str_trim(quantitative)) == "yes" ~ "Quantitative",
    tolower(str_trim(quantitative)) == "no" ~ "Qualitative",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(quant)) %>%
  distinct(study_id, quant, year)

# 2. Count studies per type, order for plotting
quant_counts <- quant_type %>%
  group_by(year, quant) %>%
  summarize(paper_count = n()) %>%
  arrange(-paper_count) %>%
  mutate(quant = fct_reorder(quant, paper_count))
quant_counts


# 3. Plotting
fig1_A <- ggplot(quant_counts, aes(x = year, y = paper_count, fill = quant)) +
  geom_col(position = position_stack(),  width = 0.7) +
  geom_text(aes(label = paper_count, y = paper_count), #vjust = -0.5, 
                position = position_stack(vjust = 0.5),  # Centered on each bar
            size = 4, fontface = "bold") +
  # Fill manual scale
  scale_fill_manual(name = NULL, 
                    values = c("Qualitative" = "#C6C1F0FF", 
                               "Quantitative" = "#F498B6FF")
                    )+
  labs(
    x = NULL,
    y = "Number of syntheses"#,
  )+
  scale_y_continuous(
  limits = c(0, 12),
  breaks = seq(0, 12, 2)
)+ 
  scale_x_continuous(breaks = seq(from=min(quant_counts$year),
                                  to=max(quant_counts$year), by =1 ) 
                     )+
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .85),
    # axis.text.x = element_text(size = 13),
    # axis.title.y = element_text(size = 12),
    panel.grid = element_blank(),
    # plot.title = element_text(size = 14, face = "bold", hjust = 0.5)
  )

fig1_A


```

## Panel B: Environment average per paper

### Simple barplot

```{r}
# Average number of environment types per paper
# sum(env_counts$paper_count)/50 
# 1.56

# 1. Process outcome categories
env <- map %>%
  select(study_id, ecosystem_type) %>%
  # Split comma-separated values and handle whitespace
  mutate(ecosystem_type = str_split(ecosystem_type, ",\\s*")) %>%  
  unnest(ecosystem_type) %>%
  filter(!is.na(ecosystem_type) & str_trim(ecosystem_type) != "")

# 2. Count papers per outcome (with sorting)
env_counts <- env %>%
  count(ecosystem_type, name = "paper_count") %>%
  arrange(-paper_count) %>%  # Sort descending
  mutate(ecosystem_type = fct_reorder(ecosystem_type, paper_count))  # For plotting

# 4. Show summary statistics
env_counts %>% 
  mutate(percentage = (paper_count/n_distinct(map$study_id))*100) %>%
  print(n = Inf)  # Show all rows

# 5. Upset plot
dat_upset_env <- env |> 
  mutate(value = 1) |> 
  pivot_wider(
    id_cols = study_id,
    names_from = ecosystem_type,
    values_from = value,
    values_fill = 0
  )

# 6. Plotting
fig1_B <- upset(
  dat_upset_env,
  intersect = colnames(dat_upset_env)[-1], 
  name = "Ecosystem type",
  base_annotations = list(
    "Intersection size" = intersection_size(
       mapping = aes(fill = 'bars_color') 
     ) + 
       annotate(
         geom = "text", x = Inf, y = Inf,
        label = paste("Average number of ecosystem types\nper study:1.56 (50 Studies)"),
          vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'), 
        guide = 'none'
      )+
  scale_y_continuous(
  limits = c(0, 20),
  breaks = seq(0, 20, 4)
)+ 
       theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),   # remove x axis title
        axis.text.x  = element_blank(),   # remove x axis text
        axis.ticks.x = element_blank() 
      )
  ),
  #Matrix dots
  matrix = intersection_matrix(
  geom = geom_point(shape = 16, size = 1.8)
),

  set_sizes = FALSE,
  min_size =0
)
  

fig1_B

```
## Panel C: Noise source average per paper

### Simple barplot

```{r}
# Average number of noise sources per paper
# sum(noise_counts$paper_count)/50 
# 2.84

# 1. Process outcome categories
noise <- map %>%
  select(study_id, noise_source) %>%
  # Split comma-separated values and handle whitespace
  mutate(noise_source = str_split(noise_source, ",\\s*")) %>%  
  unnest(noise_source) %>%
  filter(!is.na(noise_source) & str_trim(noise_source) != "")

# 2. Count papers per outcome (with sorting)
noise_counts <- noise %>%
  count(noise_source, name = "paper_count") %>%
  arrange(-paper_count) %>%  # Sort descending
  mutate(noise_source = fct_reorder(noise_source, paper_count))  # For plotting

# 3. Show summary statistics
noise_counts %>% 
  mutate(percentage = (paper_count/n_distinct(map$study_id))*100) %>%
  print(n = Inf)  # Show all rows

# 4. Upset plot
dat_upset_noise <- noise |> 
  mutate(value = 1) |> 
  pivot_wider(
    id_cols = study_id,
    names_from = noise_source,
    values_from = value,
    values_fill = 0
  )

# 5. Plotting
fig1_C <- upset(
  dat_upset_noise,
  intersect = colnames(dat_upset_noise)[-1]
   , 
   name = "Noise source",
   base_annotations = list(
     "Intersection size" = intersection_size(
       mapping = aes(fill = 'bars_color')#, 
     ) +
       annotate(
         geom = "text", x = Inf, y = Inf,
         label = paste("Average number of noise sources\nper study: 2.84 (50 Studies)"),
          vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'), 
        guide = 'none'
      )+
  scale_y_continuous(
  limits = c(0, 8),
  breaks = seq(0, 8, 2)
)+ 
       theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),   # remove x axis title
        axis.text.x  = element_blank(),   # remove x axis text
        axis.ticks.x = element_blank() 
      )
  ),
  #Matrix dots
  matrix = intersection_matrix(
  geom = geom_point(shape = 16, size = 1.8)
),

  set_sizes = FALSE,
  min_size =0
)
  

fig1_C

```
## Panel D. Outcome average per paper:

```{r}
# Average number of outcome categories per paper
# sum(outcome_counts$paper_count)
# 2.86

# 1. Process outcome categories
outcomes <- map %>%
  select(study_id, outcome_category) %>%
  # Split comma-separated values and handle whitespace
  mutate(outcome_category = str_split(outcome_category, ",\\s*")) %>%  
  unnest(outcome_category) %>%
  filter(!is.na(outcome_category) & str_trim(outcome_category) != "")

# 2. Count papers per outcome (with sorting)
outcome_counts <- outcomes %>%
  count(outcome_category, name = "paper_count") %>%
  arrange(-paper_count) %>%  # Sort descending
  mutate(outcome_category = fct_reorder(outcome_category, paper_count))  # For plotting

# 3. Show summary statistics
outcome_counts %>% 
  mutate(percentage = (paper_count/n_distinct(map$study_id))*100) %>%
  print(n = Inf)  # Show all rows

# 4. Upset plot
dat_upset_outcomes <- outcomes |> 
  mutate(value = 1) |> 
  pivot_wider(
    id_cols = study_id,
    names_from = outcome_category,
    values_from = value,
    values_fill = 0
  )

# 5. Plotting
fig1_D <- upset(
  dat_upset_outcomes,
  intersect = colnames(dat_upset_outcomes)[-1], 
  name = "Outcome categories",
  
  #Bar annotation
  base_annotations = list(
    "Intersection size" = intersection_size(
      mapping = aes(fill = 'bars_color')#, 
    ) +
      annotate(
        geom = "text", x = Inf, y = Inf,
        label = paste("Average outcomes per study:\n2.86 (50 Studies)"),
        vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'), 
        guide = 'none'
      )+
  scale_y_continuous(
  limits = c(0, 10),
  breaks = seq(0, 10, 2)
)+ 
       theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),   # remove x axis title
        axis.text.x  = element_blank(),   # remove x axis text
        axis.ticks.x = element_blank() 
      )
  ),
  #Matrix dots
  matrix = intersection_matrix(
  geom = geom_point(shape = 16, size = 1.8)
),

  set_sizes = FALSE,
  min_size =0
)
  

fig1_D

```

## Patchwork plots- Figure 1
```{r}

fig1_A <- fig1_A + labs(tag = "A")
fig1_B <- fig1_B + labs(tag = "B")
fig1_C <- fig1_C + labs(tag = "C")
fig1_D <- fig1_D + labs(tag = "D")

fig1 <- fig1_A / fig1_B / fig1_C / fig1_D +
  plot_layout(ncol = 1) &
  theme(plot.tag = element_text(size = 14, face = "bold"))

# Save plot
fig1
#ggsave(here("Figures/raw", "figure_1.pdf"), width = 11, height = 17, dpi = 300)
#ggsave(here("Figures/raw", "figure_1.png"), width = 11, height = 17, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure 2: Taxonomic groups

## Panel A: Taxonomic distribution TREEMAP

```{r}

# 1. Split and clean taxa
taxon_long4 <- map %>%
  separate_rows(scope_taxon, sep = ",") %>%
  mutate(
    scope_taxon = str_trim(scope_taxon),
    scope_taxon = str_to_title(scope_taxon)
  )

# 2. Get unique study counts per taxon (no double-counting)
taxon_counts3 <- taxon_long4 %>%
  distinct(study_id, scope_taxon) %>%
  group_by(scope_taxon) %>%
  summarise(mentions = n(), .groups = "drop")

# 3. Assign group and subgroup
 vertebrates <- c("Aves", "Mammalia", "Reptilia", "Fish", "Amphibia")

taxon_counts3 <- taxon_counts3 %>%
  mutate(
    group = if_else(scope_taxon %in% vertebrates, "Vertebrate", "Invertebrate"),
    subgroup = scope_taxon
  ) %>%
  filter(mentions > 0)

# 4. Assign pastel green and pastel purple gradients
vertebrate_subgroups <- vertebrates
invertebrate_subgroups <- setdiff(unique(taxon_counts3$subgroup), vertebrates)

# Pastel green for vertebrates pastel purple for invertebrates
pal_vertebrate <- scales::colour_ramp(c("#BBA0CA", "#600047"))(seq(0,1,length.out=length(vertebrate_subgroups)))
pal_invertebrate <- scales::colour_ramp(c("#B1B695", "#53917E"))(seq(0,1,length.out=length(invertebrate_subgroups)))

taxon_counts3 <- taxon_counts3 %>%
  mutate(
    fill_color = case_when(
      group == "Vertebrate" ~ pal_vertebrate[match(subgroup, vertebrate_subgroups)],
      group == "Invertebrate" ~ pal_invertebrate[match(subgroup, invertebrate_subgroups)]
    ),
    label = paste0(scope_taxon, "\n(", mentions, ")")
  )

# 5. Plot treemap (no subgroup label, just colored borders)
fig2 <- ggplot(taxon_counts3, aes(area = mentions, fill = fill_color, label = label, subgroup = group)) +
  geom_treemap(color = "white", size = 1.8) +
  geom_treemap_subgroup_border(color = "white", size = 3) +   # Group borders only!
  # No geom_treemap_subgroup_text()  # <--- This removes the big faded group labels
  geom_treemap_text(
    fontface = "bold", colour = "White",
    place = "bottomleft", grow = FALSE, reflow = TRUE, min.size = 6
  ) +
  scale_fill_identity() +
  #labs(
   # title = "Taxonomic scope of included studies",
   # subtitle = "Area and label = number of unique studies mentioning each taxon"
  #) +
  theme(
    plot.title = element_text(face = "bold", size = 20, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),
    legend.position = "none",
    panel.background = element_rect(fill = "white", colour = NA),
    plot.background = element_rect(fill = "white", colour = NA)
  )

fig2

#save Figure 3
#ggsave(here("Figures/raw", "Figure_2_taxa.pdf"), width = 14, height = 10, dpi= 300)
#ggsave(here("Figures/raw", "Figure_2_taxa.png"), width = 14, height = 10, dpi = 300)


```



#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 3: Annual trends

## Panel A: Outcome per time 

```{r}
# 1. Process outcomes

outcome_trends <- map %>%
  filter(!is.na(outcome_category)) %>%
  separate_rows(outcome_category, sep = ",\\s*") %>%
  mutate(outcome_category = str_trim(outcome_category)) %>%
  filter(outcome_category != "") %>%
  distinct(study_id, year, outcome_category) %>%
  count(year, outcome_category, name = "n")


# 2: Plot (horizontal stacked bar with legend circles)
fig3_a <- ggplot(outcome_trends, aes(
  x    = year, #factor(year, levels = sort(unique(year))),
  y    = n,
  fill = outcome_category
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Outcomes trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(outcome_trends$year), 
                                  to = max(outcome_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

fig3_a
```


## Panel B: Noise source

```{r}

# 1. Prepare data
noise_trends <- map %>%
  filter(!is.na(noise_source)) %>%
  separate_rows(noise_source, sep = ",") %>%
  mutate(noise_source = str_trim(noise_source)) %>%
  filter(noise_source != "") %>%
  distinct(study_id, year, noise_source) %>%
  count(year, noise_source, name = "count")

# Step 2: Plot
fig3_b <- ggplot(noise_trends, aes(
  x    = year, 
  y    = count,
  fill = noise_source
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = count),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Noise source",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
   labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(noise_trends$year), 
                                  to = max(noise_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

fig3_b
```


## Panel C: Environment

```{r}

# 1: Prepare data
ecosystem_trends <- map %>%
  filter(!is.na(ecosystem_type)) %>%
  separate_rows(ecosystem_type, sep = "[,;]") %>%
  mutate(ecosystem_type = str_trim(ecosystem_type)) %>%
  filter(ecosystem_type != "") %>%
  distinct(study_id, year, ecosystem_type) %>%
  count(year, ecosystem_type, name = "count")


# 2. Plot
fig3_c <-ggplot(ecosystem_trends, aes(
  x    = year,
  y    = count,
  fill = ecosystem_type
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = count),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Environment trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(ecosystem_trends$year), 
                                  to = max(ecosystem_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )


fig3_c

```
## Patchwork plots-Figure 3
```{r}

fig3 <- fig3_a + fig3_b + fig3_c + plot_layout(nrow = 3) + plot_annotation(tag_levels = "A")

fig3
#ggsave(here("Figures/raw", "Figure_3_trends.pdf"), width = 11, height = 10, dpi = 300)
#ggsave(here("Figures/raw", "Figure_3_trends.png"), width = 11, height = 10, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬


# Figure 4: Bibliometric analysis

## Panel A: World map with authors' affiliations
```{r}
# Load world shapefile
world <- ne_countries(scale = "medium", returnclass = "sf")

# Load bibliometric data
scopus <- biblio

colnames(scopus)
# Define functions for extraction
extract_first_last <- function(author_list) {
  authors <- strsplit(author_list, ";")[[1]]
  c(trimws(authors[1]), trimws(authors[length(authors)]))
}

extract_affiliation <- function(affiliation_list) {
  affiliations <- strsplit(affiliation_list, ";")[[1]]
  c(trimws(affiliations[1]), trimws(affiliations[length(affiliations)]))
}

extract_country <- function(affiliation) {
  tail(strsplit(affiliation, ",")[[1]], 1) %>% trimws()
}

# Define country name corrections
country_mapping <- c(
  "USA" = "United States of America",
  "USA." = "United States of America",
  "United States" = "United States of America",
  "Russian Federation" = "Russia",
  "Czech Republic" = "Czechia", 
  "United Kingdom." = "United Kingdom"
)

# Clean and recode meta-analysis data
bibs <- scopus %>%
  mutate(
    first_author = sapply(authors, \(x) extract_first_last(x)[1]),
    last_author = sapply(authors, \(x) extract_first_last(x)[2]),
    first_author_affiliation = sapply(`authors_with_affiliations`, \(x) extract_affiliation(x)[1]),
    last_author_affiliation = sapply(`authors_with_affiliations`, \(x) extract_affiliation(x)[2]),
    first_author_country = sapply(first_author_affiliation, extract_country),
    last_author_country = sapply(last_author_affiliation, extract_country),
    first_author_country = recode(first_author_country, !!!country_mapping)
  )


# Count countries
first_country_counts <- table(bibs$first_author_country) %>%
  as.data.frame() %>%
  rename(Country = Var1, First_counts = Freq)


# Join counts to world map
world_first <- world %>%
  left_join(first_country_counts, by = c("name" = "Country"))


# Plot a. (meta-analysis)
fig4_a <- ggplot(world_first) +
  geom_sf(aes(fill = First_counts), color = NA) +
  scale_fill_paletteer_c("ggthemes::Purple", 
                         na.value = "#D8D8D8FF",
                         labels = number_format(accuracy = 1)) +#[AM: set the bar scale to display integers.]
  labs(fill = "Number of first authors") + #[AM: added]
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
  ) +
  guides(fill = guide_colorbar(
    title.position = "top",
    barwidth = 15,
    barheight = 0.5
  ))

fig4_a
#ggsave(here("Figures/raw", "Figure_4_bibliomap.pdf"), width = 11, height = 10, dpi = 300)
#ggsave(here("Figures/raw", "Figure_4_bibliomap.png"), width = 11, height = 10, dpi = 300)

```


## Panel B: Chord diagram of authors collaborations
```{r}
# Load bibliometric data
dim(bib_data) 

bib_data <- metaTagExtraction(bib_data, Field = "AU1_CO", sep = ";")
bib_data <- metaTagExtraction(bib_data, Field = "AU_CO", sep = ";")
dim(bib_data)

# Generate collaboration network matrix (countries)
NetMatrix2 <- biblioNetwork(bib_data, 
                            analysis = "collaboration",
                            network = "countries", 
                            sep = ";")
net_matrix2 <- as.matrix(NetMatrix2)

# Clean country names
net_matrix2[lower.tri(net_matrix2)] <- 0  # Remove lower triangle
colnames(net_matrix2) <- str_to_title(colnames(net_matrix2))
rownames(net_matrix2) <- str_to_title(rownames(net_matrix2))
colnames(net_matrix2)[colnames(net_matrix2) == "Usa"] <- "USA"
rownames(net_matrix2)[rownames(net_matrix2) == "Usa"] <- "USA"
colnames(net_matrix2)[colnames(net_matrix2) == "United Kingdom"] <- "UK"
rownames(net_matrix2)[rownames(net_matrix2) == "United Kingdom"] <- "UK"

# Set circular layout
country_order <- names(sort(rowSums(net_matrix2), decreasing = TRUE))
net_matrix2_sorted <- net_matrix2[country_order, country_order]

# Remapped Unicorn Pro Contrast (25 countries)
cols <- c(
  "UK"                 = "#6C5FC7", # indigo
  "USA"                = "#91D3C5", # teal
  "Canada"             = "#5D5D5D", # charcoal
  "Australia"          = "#BCCF7F", # olive green
  "Netherlands"        = "#A9C7E8", # steel blue
  "Germany"            = "#C49ACF", # mauve
  "Italy"              = "#B28A85", # clay rose
  "Norway"             = "#7A8BD1", # periwinkle
  "France"             = "#6BB6C9", # teal-gray
  "Brazil"             = "#D6A9A5", # rosewood
  "China"              = "#8573C1", # muted purple
  "Spain"              = "#E8C1A8", # beige apricot
  "New Zealand"        = "#D9E7A8", # sage yellow
  "Denmark"            = "#E7D7A1", # muted gold
  "Iran"               = "#E0E0D1", # warm gray
  "Portugal"           = "#88A6D9", # dusty blue
  "Saudi Arabia"       = "#9D7ED0", # violet
  "Hong Kong"          = "#9FBBB0", # stone teal
  "Japan"              = "#CC9999", # muted coral
  "Malta"              = "#A6A6A6", # neutral gray
  "Slovenia"           = "#8E72A9", # plum
  "South Africa"       = "#B7E3D6", # pale aqua
  "Sweden"             = "#E7D7A1", # gold (slightly brighter)
  "Switzerland"        = "#BFA3D6", # lavender-gray
  "Trinidad And Tobago"= "#D7BFAF"  # pale taupe
)

# Save as PDF
#pdf(here("Figures/raw", "Figure_4b_chorddiagram.pdf"), width = 12, height = 9)

# Plot chord diagram
circos.clear()
circos.par(track.margin = c(0.01, 0.01), gap.degree = 1.5)

chordDiagram(net_matrix2_sorted,
             annotationTrack = "grid",
             annotationTrackHeight = c(0.04, 0.02),
             preAllocateTracks = 1,
             grid.col = cols)
        
circos.trackPlotRegion(track.index = 1, panel.fun = function(x, y) {
                xlim <- get.cell.meta.data("xlim")
                ylim <- get.cell.meta.data("ylim")
                sector.name <- get.cell.meta.data("sector.index")
                circos.text(mean(xlim), 
                            ylim[1] + 0.3,
                            sector.name,
                            facing = "clockwise", 
                            niceFacing = TRUE,
                            adj = c(0, 0.5), 
                            cex = 0.85)
                circos.axis(h = "bottom", labels = FALSE, major.tick = FALSE)
                            #labels.cex = 0.5)
              }, 
              bg.border = NA)

#dev.off()   # close PNG
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 5: Policy analysis, alluvial plot top 10

```{r}
# Call data
dat <- dat_policy |> 
  select(policy_topic, ecological_context, policy_document_type)

# Count combinations
dat_alluvial <- dat |> 
  group_by(policy_topic, ecological_context, policy_document_type) |> 
  summarise(Freq = n(), .groups = "drop")

# ---- Keep only top 5 most common flows ----
top5_flows <- dat_alluvial |> 
  arrange(desc(Freq)) |> 
  slice_head(n = 10)

dat_alluvial2 <- dat_alluvial |> 
  semi_join(top5_flows,
            by = c("policy_topic", "ecological_context", "policy_document_type")) |> 
  mutate(
    policy_topic        = fct_reorder(as.factor(policy_topic), Freq, .fun = sum, .desc = TRUE),
    ecological_context  = fct_reorder(as.factor(ecological_context), Freq, .fun = sum, .desc = TRUE),
    policy_document_type = fct_reorder(as.factor(policy_document_type), Freq, .fun = sum, .desc = TRUE)
  )

# Add line breaks in long labels
dat_alluvial2 <- dat_alluvial2 |>
  mutate(
    policy_document_type = fct_recode(policy_document_type,
      "Government\npolicy"       = "Government policy",
      "Regulatory\nSubmission"   = "Regulatory Submission",
      "Intergovernmental\npolicy" = "Intergovernmental policy"
    )
  )

# Colour palette
unicorn_pastel <- c(
  "Government\npolicy"        = "#D9BDE2",
  "Regulatory\nSubmission"    = "#BEECE0",
  "Intergovernmental\npolicy" = "#FFB5AA"
)
# Plot
fig5 <- ggplot(dat_alluvial2,
                       aes(axis1 = policy_document_type,
                           axis2 = ecological_context,
                           axis3 = policy_topic,
                           y = Freq)
) +
  # Reorder axes: Document type → Ecological context → Policy topic
  scale_x_discrete(
    limits = c("policy_document_type", "ecological_context", "policy_topic"),
    labels = c("Document type", "Ecological context", "Policy topic"),
    position = "top",
    expand = c(.05, .05)
  ) +
  geom_alluvium(aes(fill = policy_document_type),
                width = 1/12, alpha = 0.6) +
  geom_stratum(aes(fill = after_stat(stratum)), color = "white", linewidth = 1.2) +
  geom_text(stat = "stratum", 
            aes(label = after_stat(stratum)),
            size = 4) +
  scale_fill_manual(values = unicorn_pastel, na.value = "#f0f0f0") +
  theme_minimal(base_size = 14) +
  labs(y = NULL, x = NULL) +
  theme(
    legend.position = "none", # remove legend
    # Axis text
    axis.title.y = element_blank(),
    axis.text.y  = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x.top = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    
    # Panel and grid tweaks
    panel.grid = element_blank(),   # remove gridlines
    panel.border = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA),
    
    # Overall text and title
    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, colour = "grey30"),
    plot.caption = element_text(size = 10, colour = "grey40", hjust = 1),
    
    # Strata labels spacing
    plot.margin = margin(10, 10, 10, 10)
  )

fig5
#ggsave(here("Figures/raw", "Figure_5_alluvialplot.pdf"), width = 12, height = 9, dpi= 300)
#ggsave(here("Figures/raw", "Figure_5_alluvialplot.png"), width = 12, height = 9, dpi = 300)




```



#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 6: CEESAT scores: CEESAT question scores (all syntheses) 

```{r}
# Labels:
labels <- structure(list(q = c("1.1", "2.1", "3.1", "3.2", "4.1", "4.2", 
"4.3", "5.1", "5.2", "6.1", "6.2", "6.3", "7.1", "7.2", "7.3", 
"8.1"), label = c("1.1 Research question and criteria", 
"2.1 A priori protocol", "3.1 Systematic search approach", 
"3.2 Search comprehensiveness", "4.1 Defined eligibility criteria", 
"4.2 Consistent eligibility criteria", 
"4.3 Reported eligibility decisions", "5.1 Critical appraisal", 
"5.2 Critical appraisal cross-check", 
"6.1 Data extraction method", "6.2 Data availability?", 
"6.3 Data extraction cross-check", 
"7.1 Choice of synthesis approach", "7.2 Appropiate meta-analysis", 
"7.3 Variability investigation", 
"8.1 Synthesis limitations"
)), row.names = c(NA, -16L), class = c("tbl_df", "tbl", "data.frame"
))
labels


# Filter and select relevant columns
ceesat_long <- dat_ceesat %>%
  select(starts_with("CEESAT")) %>%
  # Convert columns with "N/A" text to numeric, which creates proper NA values
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>%
  mutate(percent = n / sum(n) * 100)

# Prepare the data for plotting. Here, we join the calculated data with the labels and set up the 'value'
# column as a factor to control the order and appearance in the plot.
ceesat_for_plot <- ceesat_long %>%
  # Create a temporary column 'q' by removing "CEESAT" from the item name
  mutate(q = str_remove(item, "CEESAT")) %>%
  # Join with the labels data frame to get descriptive labels for the plot
  left_join(labels, by = "q") %>%
  # Prepare the 'value' column for plotting
  mutate(
    value = as.character(value),
    # Replace R's NA with a string "NA" for plotting
    value = ifelse(is.na(value), "NA", value),
    # Convert 'value' to a factor to control the stacking order in the legend and bars
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )

# Plot
fig6 <- ggplot(ceesat_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5), # Center numbers on each bar segment
    size = 5,
    color = "black"
  ) +
  coord_flip() +
  scale_fill_manual(
    name = "Score",
    values = c(
      "NA" = "gray70",
      "0" = "#C73C55",
      "1" = "#DBA053",
      "3" = "#7CA982",
      "4" = "#E6D267"
    ),
    labels = c(
      "NA" = "N/A",
      "0" = "Red",
      "1" = "Amber",
      "3" = "Green",
      "4" = "Gold"
    )
  ) +
  labs(
    x = NULL, # The y-axis labels are self-explanatory
    y = "Percentage",
    fill = "Score"
  ) +
  labs(x = "CEESAT question", y = "Percentage", fill = NULL) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",        # remove legend
    panel.grid.major = element_blank(),  # remove major grid lines
    panel.grid.minor = element_blank(),  # remove minor grid lines
    axis.ticks = element_blank(),        # remove ticks
    axis.line = element_blank(),          # remove axis lines
    #increase font axis y
    axis.title.y = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    axis.text.y = element_text(size = 12), # Increase font size of question labels
    axis.text.x = element_text(size = 12)  # Increase font size of percentage labels
     )



fig6 
#ggsave(here("Figures/raw", "Figure_6_CEESAT.pdf"), width = 12, height = 9, dpi= 300)
#ggsave(here("Figures/raw", "Figure_6_CEESAT.png"), width = 12, height = 9, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Syntheses quality analysis— Cited vs not cited in policy

```{r}
# Remove NA
dat <- dat_ceesat %>%
  filter(!is.na(score_new))

# we need to change sore_new if pooled_effect_meta_an == "yes" then, divide by 64 if not, divide by 56

dat <- dat %>%
  mutate(score_new = ifelse(pooled_effect_meta_an == "yes", score_new/64, score_new/56))

#First we separate out data into policy and not policy
#the sd_bib_alt_policy is a dataframe that was previously created, maybe when Kyle did the figures to compare CEESAT for papers in policy with no cited in policy

policy <- dat$score_new[dat$cited_in_policy == "yes"]
not_policy <- dat$score_new[dat$cited_in_policy == "no"]


# Create a tibble for policy values: tibble create dataframe with two columns: values and category
policy_df <- tibble(
  values = policy,
  category = "yes" #I replace "Policy" with "1" as that is the value in my cited_in_policy column
)

# Create a tibble for not_policy values
not_policy_df <- tibble(
  values = not_policy,
  category = "no"
)

# Combine both tibbles into one
policy_combined <- bind_rows(policy_df, not_policy_df)


# Check distribution of data
hist(log(dat$score_new))

#Sensitivity check via two‐sample t‐test
# one should log it
main_analysis <- t.test(log(policy),log(not_policy)) 

main_analysis
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Supplementary figures
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

### Figure S3: Academic citation count and the three most cited syntheses
```{r}
# 1. Create empty label column
biblio$label <- NA

# 2. Assign labels to the three top-cited papers
biblio$label[grepl("Benítez-López", biblio$authors) & biblio$year == 2010] <- "Benítez-López et al., 2010"
biblio$label[grepl("Shannon",       biblio$authors) & biblio$year == 2016] <- "Shannon et al., 2016"
biblio$label[grepl("Duarte",        biblio$authors) & biblio$year == 2021] <- "Duarte et al., 2021"

# 3. Make the citation scatterplot
fig_S3 <- ggplot(biblio, aes(x = year, y = cited_by)) +
  geom_jitter(size = 4.3, alpha = 0.25, color = "#8074A8FF", width = 0.3, height = 0) +
  geom_point(data = subset(biblio, !is.na(label)), 
             aes(x = year, y = cited_by), 
             color = "#8074A8FF", size = 4.3) +
  geom_label(data = subset(biblio, !is.na(label)), 
             aes(label = label), 
             hjust = -0.1, vjust = 0.4, size = 3.5,
             fill = "white", color = "black"
  ) +
   labs(
     x = NULL,
    y = "Academic citation count"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(biblio$year), 
                                  to = max(biblio$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .75),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )
  
 
 
# 4. Print plot
fig_S3

#Save
#ggsave(here("Figures/raw", "Figure_S3_academic_citatation_count.pdf"), width = 10, height = 7, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S3_academic_citation_count.png"), width = 16, height = 10, dpi= 300)  


```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S4- Keywords
## Panel A: keyword bargraph
```{r}
# ---- Parameters ----
# Split by semi colon and then calculate frequency
dt.long <- biblio %>%
  select(author_keywords, index_keywords, doi) %>%
  pivot_longer(cols = c("author_keywords", "index_keywords")) %>%
  separate_longer_delim(col = "value",
                        delim = ";")
dt.long

#---------Create a synonnym diccionary -----------
synonyms <- c(
  # Meta-analysis variants
  "Meta Analysis"     = "Meta-Analysis",
  "Meta Analyses"     = "Meta-Analysis",
  "Literature Review" = "Review",
  
  # Fish variants
  "Fishes"            = "Fish",
  "Fishing"            = "Fishery",
  "Fish Physiology" = "Fish",
  "Fish Behaviour"    = "Fish",
  "Fishery"           = "Fishery",
  "Fisheries"           = "Fishery",
  "Pisces"            = "Fish",
  "Aquatic Organisms" = "Aquatic Species",
  "Aquatic Species" = "Aquatic Species",
  
  # Marine environment
  "Marine Soundscape" = "Marine",
  "Marine" = "Marine",
  "Marine Ecosystem" = "Marine Ecosystem",
  "Marine Ecosystems" = "Marine Ecosystem",
  "Marine Environment" = "Marine Ecosystem",
  "Marine Environments" = "Marine Ecosystem",
  "Marine vessels" = "Marine Vessel",
  "Marine vessel" = "Marine Vessel",
  "Vessel" = "Marine Vessel",
  "Vessels" = "Marine Vessel",
  "Ship" = "Marine Vessel",
  "Shipping" = "Marine Vessel",
  
  
  
  # Mammal variants
  "Mammals"           = "Mammal",
  "Mammalia"          = "Mammal",
  
  # Bird variants
  "Birds"             = "Bird",
  "Aves"              = "Bird",
  
  # Invertebrate variants
  "Invertebrates"     = "Invertebrate",
  "Invertebrata"      = "Invertebrate",
  
  # Animal variants
  "Animal"            = "Animals",
  "Fauna"            = "Animals",
  "Animalia"          = "Animals",
  "Wild Animal"       = "Wildlife",
  "Animals, Wild"     = "Wildlife",
  "Behavior, Animal"     = "Behaviour",
  "Behaviour, Animal"     = "Behaviour",
  "Behavioural"     = "Behaviour",
  "Behavior"  = "Behaviour",
  "Behavioral"  = "Behaviour",
  
  
  # Human variants
  "Humans"            = "Human",
  
  # Cetacean variants
  "Cetacea"           = "Cetaceans",
  "Cetacean"          = "Cetaceans",
  
  # Whale variants
  "Whales"            = "Whale",
  "Beluga Whales"     = "Beluga Whale",
  "Bowhead Whales"    = "Bowhead Whale",
  
  # Dolphin variants
  "Dolphins"          = "Dolphin",
  
  # Noise variants
  "Noise Impact"      = "Noise",
  "Noise-Induced Stress" = "Stress",
  
  # Anthropogenic noise variants
  "Anthrophony"       = "Anthropophony",
  "Anthropogenic Sounds" = "Anthropogenic Sound",
  "Anthropogenic Pollutants" = "Anthropogenic Pollutant",
  "Human-Induced Environmental Change" = "Human Disturbance",
  "Human Disturbances" = "Human Disturbance",
  "Human Disturbance" = "Human Disturbance",
  "Human Activities" = "Human Activity",
  "Human Activity" = "Human Activity",
  
  
  # Pollution variants
  "Sound Pollution"   = "Noise Pollution",
  "Acoustic Pollution"= "Noise Pollution",
  "Contaminación Por Ruido" = "Noise Pollution",
  "Contaminación Sonora"    = "Noise Pollution",
  "声污染"                 = "Noise Pollution",
  "噪音污染"                = "Noise Pollution",
  
  # Urbanization variants
  "Urbanización"      = "Urbanization",
  "城市化"              = "Urbanization",
  
  # Vertebrate variants
  "Vertebrates"       = "Vertebrate",
  "Vertebrata"        = "Vertebrate",
  
  # Review variants
  "Systematic Maps"   = "Systematic Map",
  "Systematic Literature Review" = "Systematic Review",
  "Scoping Review"    = "Scoping Review",
  "Review"            = "Review",
  
  # Risk variants
  "Risks Assessments" = "Risk Assessment",
  "Risk Evaluation"   = "Risk Assessment",
  # Environmental variants
  "Ecosystems" = "Ecosystem",
  "Ecosystem" = "Ecosystem",
  "Ecosystems" = "Ecosystem",
  "Environmental" = "Environment",
  "Environment" = "Environment",
  "Environmental Impacts" = "Environmental Impact",
  "Environmental Impact" = "Environmental Impact",
  "Environmental Disturbance" = "Environmental Impact",
  "Environmental Change" = "Environmental Impact",
  "Environmental Effect" = "Environmental Impact",
  "Environmental Fate" = "Environmental Impact",
  "Environmental Stressors" = "Environmental Stress",
  "Environmental Stress" = "Environmental Stress",
  "Environmental Impact Analysis" = "Environmental Impact Assessment",
  "Environmental Impacts Analysis" = "Environmental Impact Assessment",
  "Environmental Impact Assessments" = "Environmental Impact Assessment",
  "Environmental Policies" = "Environmental Policy",
  "Environmental Policy" = "Environmental Policy",
  "Conservation" = "Conservation",
  "Conservation Management" = "Conservation"

)

# ----Standardize case, trim whitespace ----
dt.long <- dt.long %>%
  mutate(value = str_to_title(value)) %>%
  mutate(value = trimws(value)) %>%
# Apply synonyms dictionary 
  mutate(value = recode(value, !!!synonyms)) %>%
# drop NA
  filter(!is.na(value) & value != "")
# sort unique values
  sort(unique(dt.long$value))

# calculate number of mentions of each keyword—frequencies
keyword.freq <- dt.long %>%
  group_by(value) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

#-------Diagnostics-------
## number of mentions, including repeats
  nrow(dt.long)
## number of unique keywords after grouping
  nrow(keyword.freq)
## unique keyword count
  length(unique(dt.long$value))

## Find mising data
#setdiff(unique(dt.long$value), keyword.freq$value)

keyword.freq <- keyword.freq %>%
  arrange(-n)

# Clean NA
keyword.freq_clean <- keyword.freq %>%
  filter(!is.na(value))

# Reorder factor levels based on frequency for plotting
keyword.freq$value <- factor(keyword.freq$value,
                             levels = rev(keyword.freq$value))

# Plot
fig_S4A <- ggplot(data = keyword.freq[1:20, ],
                    aes(x = n, y = value, fill = n))+
  geom_col()+
  scale_fill_gradient(low = "#B4D8E4", high = "#00425E")+
  xlab("Number of keywords")+
  ylab("Keyword")+
  #theme_bw()
  theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.y = element_blank(),   # remove x axis title
        #axis.text.y  = element_blank(),   # remove x axis text
        axis.ticks.x = element_blank() 
      )

fig_S4A

#Save
#ggsave(here("Figures/raw", "Figure_S4A_Keywords.pdf"), width = 12, height = 8, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S4A_Keyords.png"), width = 12, height = 8, dpi= 300)

```
## Panel B - Cloud map

```{r}
# Extract a palette as a vector of hex colors
pal <- paletteer::paletteer_d("ggthemes::Purple_Pink_Gray")

# Convert to character (paletteer objects are special class)
pal <- as.character(pal)

# Word map
fig_S4B <- wordcloud2(keyword.freq, 
                      size = 1, 
                      color = pal, 
                      backgroundColor = "white",
                      shape = "rectangle"
)

fig_S4B
```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S5: Policy trends

## Panel A: Policy topic trends

```{r}
# Step 1: Process outcomes
policytopic <- dat_policy %>%
  filter(!is.na(policy_document_type)) %>%
  #separate_rows(policy_topic, sep = ",\\s*") %>%
  mutate(policytopic = str_trim(policy_topic)) %>%
  filter(policy_topic != "") %>%
  distinct(study_id, policy_year, policy_topic) %>%
  count(policy_year, policy_topic, name = "n")

# Step 3: Plot (horizontal stacked bar with legend circles)
figS5_a <- ggplot(policytopic, aes(
  x = policy_year,,
  y    = n,
  fill = policy_topic
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy topic trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"
  ) +
  scale_x_continuous(breaks = seq(from = min(policytopic$policy_year), 
                                  to = max(policytopic$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )
figS5_a

```


## Panel B: Policy ecological context trends

```{r}
# Step 1: Read data and process outcomes
# df <- read_csv(here("Data", "policy.csv"))

policy_eco <- dat_policy %>%
  filter(!is.na(ecological_context)) %>%
  #separate_rows(ecological_context, sep = ",\\s*") %>%
  mutate(ecological_context = str_trim(ecological_context)) %>%
  filter(ecological_context != "") %>%
  distinct(study_id, policy_year, ecological_context) %>%
  count(policy_year, ecological_context, name = "n")

# Step 3: Plot (horizontal stacked bar with legend circles)
figS5_b <- ggplot(policy_eco, aes(
  x    = policy_year,
  y    = n,
  fill = ecological_context
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy ecosystem trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(policy_eco$policy_year), 
                                  to = max(policy_eco$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

figS5_b
```
## Panel C: Policy document type trends 

```{r}
# Manage data
policytype <- dat_policy %>%
  filter(!is.na(policy_document_type)) %>%
  #separate_rows(policy_document_type, sep = ",\\s*") %>%
  mutate(policy_document_typet = str_trim(policy_document_type)) %>%
  filter(policy_document_type != "") %>%
  distinct(study_id, policy_year, policy_document_type) %>%
  count(policy_year, policy_document_type, name = "n")



# Step 3: Plot (horizontal stacked bar with legend circles)
figS5_c <- ggplot(policytype, aes(
  x    = policy_year,
  y    = n,
  fill = policy_document_type
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy document type trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"
  ) +
  scale_x_continuous(breaks = seq(from = min(policytype$policy_year), 
                                  to = max(policytype$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

figS5_c
```

## Patchwork-Figure 6
```{r}

figS5 <- figS5_a + figS5_b + figS5_c + plot_layout(nrow = 3) + plot_annotation(tag_levels = "A")

figS5
#ggsave(here("Figures/raw", "Figure_S5_trends.pdf"), width = 11, height = 12, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S5_trends.png"), width = 11, height = 12, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

## Figure S6: Policy citation publication year of the REVIEW and the total policy citation
```{r}
# filter by policy cited or not
pol_fil <- pol_ci %>% 
  filter(policy_cited == "Yes")

colnames(pol_fil)

# 3. Create empty label column
pol_cit <- pol_fil %>%
  mutate(label = case_when(
    study_id == "benitez_2010" ~ "Benítez-López et al., 2010",
    study_id == "shannon_2016" ~ "Shannon et al., 2016",
    TRUE ~ NA_character_
  ))



# 4. Make the citation scatterplot
fig_S6 <- ggplot(pol_cit, aes(x = year, y = unique_policy_citations)) +
  geom_jitter(size = 4.3, alpha = 0.25, color = "#8074A8FF", width = 0.3, height = 0) +
  geom_point(data = subset(pol_cit, !is.na(label)), 
             aes(x = year, y = unique_policy_citations), 
             color = "#8074A8FF", size = 4.3) +
  geom_label(data = subset(pol_cit, !is.na(label)), 
             aes(label = label), 
             hjust = -0.1, vjust = 0.4, size = 3.5,
             fill = "white", color = "black"
  ) +
   labs(
     x = NULL,
    y = "Policy documents citing syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(pol_cit$year), 
                                  to = max(pol_cit$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .75),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )
  
 
 
# 5. Print plot
fig_S6

#Save
#ggsave(here("Figures/raw", "Figure_S6_policyciting.pdf"), width = 10, height = 7, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S6_policyciting.png"), width = 10, height = 7, dpi = 300)
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S7: Policy analysis, alluvial plot all variables

```{r}
# Alluvial plot with consistent pastel colors by Document Type ----
dat <- dat_policy |> 
  select(policy_topic, ecological_context, policy_document_type)

dat_alluvial <- dat |> 
  group_by(policy_topic, ecological_context, policy_document_type) |> 
  summarise(Freq = n(), .groups = "drop")

# Prefix axis labels for uniqueness and reorder by frequency
dat_alluvial2 <- dat_alluvial |>
  mutate(
    policy_topic        = fct_reorder(as.factor(policy_topic), Freq, .fun = sum, .desc = TRUE),
    ecological_context  = fct_reorder(as.factor(ecological_context), Freq, .fun = sum, .desc = TRUE),
    policy_document_type = fct_reorder(as.factor(policy_document_type), Freq, .fun = sum, .desc = TRUE)
  ) |>
  # 🔑 Wrap long labels in Document type only
  mutate(
    policy_document_type = fct_relabel(policy_document_type, ~ str_replace_all(.x, 
                                                                      c("Government policy"        = "Government\npolicy",
                                                                        "Regulatory Submission"    = "Regulatory\nSubmission",
                                                                        "Intergovernmental policy" = "Intergovernmental\npolicy")))
  )


# Unicorn pastel palette (keys must match new labels)
unicorn_pastel <- c(
  "Government\npolicy"        = "#D9BDE2",
  "Regulatory\nSubmission"    = "#BEECE0",
  "Intergovernmental\npolicy" = "#FFB5AA",
  "NGO report"                = "#B7D9EB",
  "Think Tank"                = "#D6D6F8",
  "Academic advisory"        = "#FFE3A3",
  "Other document"           = "#B6E06E"
)

# ---- Plot ----
figS7 <- ggplot(dat_alluvial2,
                       aes(axis1 = policy_document_type,
                           axis2 = ecological_context,
                           axis3 = policy_topic,
                           y = Freq)
) +
  scale_x_discrete(
    limits = c("policy_document_type", "ecological_context", "policy_topic"),
    labels = c("Document type", "Ecological context", "Policy topic"),
    position = "top",
    expand = c(.05, .05)
  ) +
 geom_alluvium(aes(fill = policy_document_type),
                width = 1/12, alpha = 0.8, knot.pos = 0.4) +
  geom_stratum(aes(fill = after_stat(stratum)), 
               color = "white", linewidth = 1.2, width = 0.2) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 4) +
  scale_fill_manual(values = unicorn_pastel, na.value = "#f0f0f0") +
  
  theme_minimal(base_size = 14) +
  labs(y = "Count of papers", x = NULL) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.y  = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x.top = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA),
    plot.margin = margin(10, 10, 10, 10)
  )


figS7
#ggsave(here("Figures/raw", "Figure_S7_alluvialplot.pdf"), width = 10, height = 10, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S7_alluvialplot.png"), width = 10, height = 10, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S8 - Geographical distribution of policy

## Panel A: Geographical distribution policy map
```{r}
policy_counts <- dat_policy %>%
  mutate(policy_country_clean = case_when(
    policy_country %in% c("Northern Ireland", "Scotland", "United Kingdom") ~ "United Kingdom",
    policy_country %in% c("USA", "U.S.A.", "United States") ~ "United States of America",
    TRUE ~ policy_country
  )) %>%
  filter(policy_country_clean != "International") %>%
  count(policy_country_clean, name = "n", sort = TRUE)

# Get the base count for the EU
eu_base_count <- policy_counts %>%
  filter(policy_country_clean == "European Union") %>%
  pull(n)

# Get the counts for individual countries
country_specific_counts <- policy_counts %>%
  filter(policy_country_clean != "European Union")
# ----------------------------------------------------
# CREATE FINAL COUNTS
# ----------------------------------------------------
world <- ne_countries(scale = "medium", returnclass = "sf")

map_data <- world %>%
  left_join(country_specific_counts, by = c("name" = "policy_country_clean")) %>%
  mutate(is_eu = !is.na(countrycode(name, "country.name", "eu28"))) %>%
  mutate(n_final = case_when(
    # For EU countries that ALSO have their own policies (e.g., Germany), ADD the counts.
    is_eu & !is.na(n) ~ n + eu_base_count,
    # For EU countries with NO specific policies, use the base EU count.
    is_eu & is.na(n)  ~ eu_base_count,
    # For non-EU countries, just use their own count.
    !is_eu            ~ n,
    # A fallback for any other case
    TRUE              ~ n
  ))

# PLOT THE MAP
fig_S8a <- ggplot(data = map_data) +
  geom_sf(aes(fill = n_final), color = NA) + 
  scale_fill_paletteer_c("ggthemes::Purple",
                         na.value = "#D8D8D8FF",
                         labels = number_format(accuracy = 1)) +
  labs(
    fill = "Combined policy count", # <-- Updated label for clarity
    caption = "EU countries are shown with a base count of 24, plus any country-specific counts."
  ) +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.caption = element_text(hjust = 0.5, size = 8, margin = margin(t = 5)) # Style the caption
  ) +
  guides(fill = guide_colorbar(
    title.position = "top",
    barwidth = 15,
    barheight = 0.5
  ))


fig_S8a
#ggsave(here("Figures/raw", "Figure_S8a_map_policy_countries.pdf"), width = 16, height = 14)
#ggsave(here("Figures/raw", "Figure_S8a_map_policy_countries.png"), width = 16, height = 14, dpi = 300)
```



## Panel B: Top 10 policy document countries
```{r}
# Clean policy_country
dat_policy <- dat_policy %>%
  mutate(policy_country = case_when(
    policy_country %in% c("Northern Ireland", "Scotland", "United Kingdom") ~ "United Kingdom",
    TRUE ~ policy_country
  ))

# Clean and count countries
policy_country <- dat_policy %>%
  filter(!is.na(policy_country)) %>%
  mutate(policy_country = str_trim(policy_country)) %>%
  filter(policy_country != "") %>%
  #distinct(study_id, year, policy_country) %>%
  count(policy_country, name = "count")

# top 10
policy_country_top10 <- policy_country %>%
  slice_max(count, n = 10)

# Plot
fig_S8b <- ggplot(policy_country_top10, 
       aes(x = reorder(policy_country, count),
           y = count,
           fill = policy_country)
       ) +
    geom_col(fill = "#8074A8FF", width = 0.9) +
    geom_text(aes(label = count), 
              hjust = 1.2, colour = "white", size = 5
              ) +
    labs(
        #title = "Policy document countries",
        x = NULL,
        y = "Policy documents count"
    ) +
   theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
    legend.position = "inside",
    #legend.position.inside = c(.15, .65),
    #legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
  )+
  coord_flip()


fig_S8b
#ggsave(here("Figures/raw", "Figure_S8b_toppol_countries.pdf"), width = 11, height = 8, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S8b_toppol_countries.png"), width = 11, height = 8, dpi = 300)
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S9: Annual trends cited and not cited in policy

```{r}
# Tidy data
tidy_trends <- map %>%
  select(study_id, year, cited_policy, outcome_category, noise_source, ecosystem_type) %>%
  pivot_longer(
    cols = c(outcome_category, noise_source, ecosystem_type),
    names_to = "category_group",
    values_to = "category_value"
  ) %>%
  filter(!is.na(category_value), category_value != "") %>%
  separate_rows(category_value, sep = "[,;]\\s*") %>%
  mutate(category_value = str_trim(category_value)) %>%
  
  # --- NEW: Filter out "NA" values as requested ---
  filter(category_value != "NA") %>%
  
  group_by(year, cited_policy, category_group, category_value) %>%
  summarise(n = n_distinct(study_id), .groups = "drop")

# Plotting function
create_trend_plot <- function(df, legend_title, plot_title = NULL) {
  
  ggplot(df, aes(x = year, y = n, fill = category_value)) +
    geom_col(width = 0.8, position = position_stack()) +
    
    # Count for each segment inside the bar
    geom_text(
      aes(label = n),
      position = position_stack(vjust = 0.5),
      size = 2.5,
      colour = "white",
      fontface = "bold"
    ) +
    
    scale_fill_paletteer_d("ggthemes::Purple_Pink_Gray", name = legend_title) +
    scale_x_continuous(
      breaks = seq(2008, 2025, 1),
      limits = c(2008, 2025)
    ) +
    scale_y_continuous(
      limits = c(0, 30),
      breaks = seq(0, 30, 5)
  )+ 
    labs(
      title = plot_title, # Title will be applied only if provided
      x = NULL,
      y = "Number of syntheses"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.title = element_text(face = "bold", size = 10),
      legend.text = element_text(size = 9),
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5) # Larger title
    )
}


```

### Patchwork
```{r}
# --- STEP 3: CORRECTED FINAL ASSEMBLY ---


p_A <- tidy_trends %>%
  filter(category_group == "outcome_category", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Outcome", plot_title = "Cited in Policy") +
  theme(legend.position = "none")

p_B <- tidy_trends %>%
  filter(category_group == "outcome_category", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Outcome", plot_title = "Not Cited in Policy") +
  theme(legend.position ="inside")

p_C <- tidy_trends %>%
  filter(category_group == "noise_source", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Noise Source") +
  theme(legend.position = "none")

p_D <- tidy_trends %>%
  filter(category_group == "noise_source", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Noise Source") +
  theme(legend.position ="inside")

p_E <- tidy_trends %>%
  filter(category_group == "ecosystem_type", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Environment") +
  theme(legend.position = "none")

p_F <- tidy_trends %>%
  filter(category_group == "ecosystem_type", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Environment") +
  theme(legend.position ="inside")

# --- ASSEMBLE THE FINAL FIGURE (REVISED LOGIC) ---

# Row 1: X-axis is now visible. Legend position is controlled here.
row1 <- p_B + 
        (p_A + theme(axis.title.y = element_blank())) +
        plot_layout(guides = "collect") #& theme(legend.position = 'inside')

# Row 2: X-axis is now visible. Legend position is controlled here.
row2 <- p_D + 
        (p_C + theme(axis.title.y = element_blank())) +
        plot_layout(guides = "collect") #& theme(legend.position = 'inside')
        
# Row 3: X-axis was always visible. Legend position is controlled here.
row3 <- p_F + 
        (p_E + theme(axis.title.y = element_blank())) +
        plot_layout(guides = "collect") #& theme(legend.position = 'inside')

# Combine the three rows vertically and add the A-F panel tags
final_figure_corrected <- (row1 / row2 / row3) +
  plot_annotation(tag_levels = 'A')

# Display the corrected figure
final_figure_corrected

# To save the figure
ggsave(here("Figures/raw", "Final_fig_trends.pdf"), width = 20, height = 18, dpi = 300)
ggsave(here("Figures/raw", "Final_fig_trends.png"), width = 20, height = 18, dpi = 300)

```






## Panel A: Outcome per time cited in policy
```{r}

# Filter and select relevant columns
outcome_trends <- map %>%
  filter(cited_policy == "yes") %>% # filter cited in policy
  filter(!is.na(outcome_category)) %>%
  separate_rows(outcome_category, sep = ",\\s*") %>%
  mutate(outcome_category = str_trim(outcome_category)) %>%
  filter(outcome_category != "") %>%
  distinct(study_id, year, outcome_category, cited_policy) %>%
  count(year, outcome_category, cited_policy, name = "n")


# Step 3: Plot (horizontal stacked bar with legend circles)
fig_S9a <- ggplot(outcome_trends,
  aes(
  x    = year, #factor(year, levels = sort(unique(year))),
  y    = n,
  fill = outcome_category
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Outcomes trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Cited in policy"
  ) +
  scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+ 
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )


fig_S9a
```



## Panel B: Outcometrends not cited in policy
```{r}
# Filter and select relevant columns
outcome_trends <- map %>%
  filter(cited_policy == "no") %>% # filter cited in policy
  filter(!is.na(outcome_category)) %>%
  separate_rows(outcome_category, sep = ",\\s*") %>%
  mutate(outcome_category = str_trim(outcome_category)) %>%
  filter(outcome_category != "") %>%
  distinct(study_id, year, outcome_category) %>%
  count(year, outcome_category, name = "n")


# Step 3: Plot (horizontal stacked bar with legend circles)
fig_S9b <- ggplot(outcome_trends,  # <- first argument = data
  aes(
    x    = year,
    y    = n,
    fill = outcome_category
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Outcomes trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Not cited in policy"
  ) +
   scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+ 
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

fig_S9b

```


## Panel C: Noise source cited in policy

```{r}
# Step 1: Prepare data
# Filter and select relevant columns
noise_trends <- map %>%
  filter(cited_policy == "yes") %>%
  filter(!is.na(noise_source)) %>%
  separate_rows(noise_source, sep = ",") %>%
  mutate(noise_source = str_trim(noise_source)) %>%
  filter(noise_source != "") %>%
  distinct(study_id, year, noise_source) %>%
  count(year, noise_source, name = "n")


# Step 3: Plot
fig_S9c <- ggplot(noise_trends, 
  aes(
  x    = year, #factor(year, levels = sort(unique(year))),
  y    = n,
  fill = noise_source
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Noise source",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
   labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Cited in policy"
  ) +
   scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+ 
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

fig_S9c

```

## Panel D: Noise source not cited in policy

```{r}
# Load your data
# Filter and select relevant columns
noise_trends <- map %>%
  filter(cited_policy == "no") %>%
  filter(!is.na(noise_source)) %>%
  separate_rows(noise_source, sep = ",") %>%
  mutate(noise_source = str_trim(noise_source)) %>%
  filter(noise_source != "") %>%
  distinct(study_id, year, noise_source) %>%
  count(year, noise_source, name = "n")

# Plot
fig_S9d <- ggplot(noise_trends, aes(
  x    = year, #factor(year, levels = sort(unique(year))),
  y    = n,
  fill = noise_source
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Noise source",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
   labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Not cited in policy"
  ) +
scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+ 
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )

fig_S9d

```

## Panel E: Environment cited in policy

```{r}
# Prepare data
ecosystem_trends <- map %>%
  filter(cited_policy == "yes") %>%
  filter(!is.na(ecosystem_type)) %>%
  separate_rows(ecosystem_type, sep = "[,;]") %>%
  mutate(ecosystem_type = str_trim(ecosystem_type)) %>%
  filter(ecosystem_type != "") %>%
  distinct(study_id, year, ecosystem_type) %>%
  count(year, ecosystem_type, name = "n")

# Step 3: Plot
fig_S9e <-ggplot(ecosystem_trends, aes(
  x    = year, #factor(year, levels = sort(unique(year))),
  y    = n,
  fill = ecosystem_type
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Environment trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Cited in policy"
  ) +
  scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+  
  
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )


fig_S9e

```


## Panel F: Environment not cited in policy

```{r}
# Step 1: Prepare data
ecosystem_trends <- map %>%
  filter(cited_policy == "no") %>%
  filter(!is.na(ecosystem_type)) %>%
  separate_rows(ecosystem_type, sep = "[,;]") %>%
  mutate(ecosystem_type = str_trim(ecosystem_type)) %>%
  filter(ecosystem_type != "") %>%
  distinct(study_id, year, ecosystem_type) %>%
  count(year, ecosystem_type, name = "n")


# Step 3: Plot
fig_S9f <-ggplot(ecosystem_trends, aes(
  x    = year,
  y    = n,
  fill = ecosystem_type
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Environment trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses",
    title = "Not cited in policy"
  ) +
scale_x_continuous(
  breaks = seq(2008, 2025, 1),
  limits = c(2008,2025)
  )+ 
scale_y_continuous(
  limits = c(0, 30),
  breaks = seq(0, 30, 5)
)+                   
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
    
  )


fig_S9f
```


## Patchwork-Figure S9
```{r}

figS91 <- (fig_S9a + (fig_S9b + 
                        theme(axis.title.y = element_blank())) + 
  plot_layout(nrow = 1, guides = "collect")+
  theme(legend.position = "left",
  legend.position.inside = c(0.15, 0.65)))
  
  
  
figS92 <- (fig_S9c + (fig_S9d+ 
                        theme(axis.title.y = element_blank())) + 
  plot_layout(nrow = 1, guides = "collect")+
  plot_annotation(tag_levels ="A")+
  theme(legend.position = "left",
        legend.position.inside = c(0.15, 0.65)))



figS93 <- (fig_S9e + (fig_S9f+ 
                        theme(axis.title.y = element_blank())) + 
  plot_layout(nrow = 1, guides = "collect")+
  plot_annotation(tag_levels ="A")+
  theme(legend.position = "left",
        legend.position.inside = c(0.15, 0.65)))


figureS9 <- figS91 / figS92 / figS93 +  
              plot_layout(nrow = 3) + #guides = "collect") + 
              plot_annotation(tag_levels = "A") &
               theme(legend.position = "right")
    
# Save
figureS9
ggsave(here("Figures/raw", "Figure_S9_trends.pdf"), width = 20, height = 18, dpi = 300)
ggsave(here("Figures/raw", "Figure_S9_trends.png"), width = 20, height = 18, dpi = 300)

```




#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S10 - CEESAT scores cited and not cited in policy

## Panel A: CEESAT scores (syntheses cited in policy):

```{r}
# 1. Labels
labels <- structure(list(q = c("1.1", "2.1", "3.1", "3.2", "4.1", "4.2", 
"4.3", "5.1", "5.2", "6.1", "6.2", "6.3", "7.1", "7.2", "7.3", 
"8.1"), label = c("1.1 Research question and criteria", 
"2.1 A priori protocol", "3.1 Systematic search approach", 
"3.2 Search comprehensiveness", "4.1 Defined eligibility criteria", 
"4.2 Consistent eligibility criteria", 
"4.3 Reported eligibility decisions", "5.1 Critical appraisal", 
"5.2 Critical appraisal cross-check", 
"6.1 Data extraction method", "6.2 Data availability?", 
"6.3 Data extraction cross-check", 
"7.1 Choice of synthesis approach", "7.2 Appropiate meta-analysis", 
"7.3 Variability investigation", 
"8.1 Synthesis limitations"
)), row.names = c(NA, -16L), class = c("tbl_df", "tbl", "data.frame"
))


# 2. Prepare the data for BOTH plots
# Data for CITED plot
ceesat_cited_for_plot <- dat_ceesat %>%
  filter(cited_in_policy == "yes") %>%
  select(starts_with("CEESAT")) %>%
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>% summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>% mutate(percent = n / sum(n) * 100) %>%
  mutate(q = str_remove(item, "CEESAT")) %>%
  left_join(labels, by = "q") %>%
  mutate(
    value = as.character(value),
    value = ifelse(is.na(value), "NA", value),
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )

# Data for NOT CITED plot
ceesat_not_cited_for_plot <- dat_ceesat %>%
  filter(cited_in_policy == "no") %>%
  select(starts_with("CEESAT")) %>%
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>% summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>% mutate(percent = n / sum(n) * 100) %>%
  mutate(q = str_remove(item, "CEESAT")) %>%
  left_join(labels, by = "q") %>%
  mutate(
    value = as.character(value),
    value = ifelse(is.na(value), "NA", value),
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )


# 3. Create the individual plots with updated themes
common_theme <- theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(), 
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 14) # Increase percentage label size for both plots
  )

# Plot A: Cited
figS10_a <- ggplot(ceesat_cited_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 5, color = "black") +
  coord_flip() +
  scale_fill_manual(name = "Score", values = c("NA" = "gray70", "0" = "#C73C55", "1" = "#DBA053", "3" = "#7CA982", "4" = "#E6D267"),
                    labels = c("NA" = "N/A", "0" = "Red", "1" = "Amber", "3" = "Green", "4" = "Gold")) +
  labs(x = NULL, y = NULL) + 
  common_theme +
  # ---- THIS LINE INCREASES THE QUESTION FONT SIZE ----
  theme(axis.text.y = element_text(size = 14)) 

# Plot B: Not Cited
figS10_b <- ggplot(ceesat_not_cited_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 5, color = "black") +
  coord_flip() +
  scale_fill_manual(name = "Score", values = c("NA" = "gray70", "0" = "#C73C55", "1" = "#DBA053", "3" = "#7CA982", "4" = "#E6D267"),
                    labels = c("NA" = "N/A", "0" = "Red", "1" = "Amber", "3" = "Green", "4" = "Gold")) +
  labs(x = NULL, y = NULL) + 
  common_theme +
  theme(axis.text.y = element_blank())

figS10_a
figS10_b

```
## Patchwork- Figure S10 CEESAT
```{r}

figS10 <- (figS10_a | figS10_b) +
  plot_annotation(
    tag_levels = 'A',
    caption = 'Percentage'
  ) & 
  theme(
    legend.position = "none",
    plot.caption = element_text(hjust = 0.6, size = 14) 
  )      

# 5. Display the final combined plot
figS10
#ggsave(here("Figures/raw", "Figure_S10_CEESATcited_notcited.pdf"), width = 16, height = 9, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S10_CEESATcited_notcited.png"), width = 16, height = 9, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Packages citations

```{r}
# List of packages
pkgs <- c(
  "tidyverse","ggplot2","here","stringr","paletteer","readr","dplyr","forcats",
  "scales","treemapify","rphylopic","RColorBrewer","viridis","tidyr","mapproj",
  "bibliometrix","viridisLite","treemap","ComplexUpset","patchwork","wordcloud2",
  "janitor","textstem","SnowballC","webshot","countrycode","sf","rnaturalearthdata",
  "rnaturalearth","ggrepel","packcircles","ggforce", "tidyverse", "sf"
)

# Function to safely get BibTeX citation
get_bib <- function(pkg) {
  tryCatch(
    toBibtex(citation(pkg)), 
    error = function(e) paste0("% Error getting citation for: ", pkg, "\n")
  )
}

# Collect citations
bibs <- lapply(pkgs, get_bib)

# Flatten list into a single character vector
bibs_text <- unlist(bibs)

# Write to file
writeLines(bibs_text, "Rpackages_citations.bib")

message("Bib file created: Rpackages_citations.bib")

```
```{r}
# List of packages
pkgs <- c(
  "tidyverse","ggplot2","here","stringr","paletteer","readr","dplyr","forcats",
  "scales","treemapify","rphylopic","RColorBrewer","viridis","tidyr","mapproj",
  "bibliometrix","viridisLite","treemap","ComplexUpset","patchwork","wordcloud2",
  "janitor","textstem","SnowballC","webshot","countrycode","sf","rnaturalearthdata",
  "rnaturalearth","ggrepel","packcircles","ggforce", "sf"
)

# Get versions
pkg_versions <- sapply(pkgs, function(pkg) {
  tryCatch(as.character(packageVersion(pkg)), error = function(e) NA)
})

# Print neatly
print(pkg_versions)

# Optionally export to CSV
versions_df <- data.frame(
  Package = names(pkg_versions),
  Version = unname(pkg_versions),
  stringsAsFactors = FALSE
)

#write.csv(versions_df, "Rpackages_versions.csv", row.names = FALSE)

#message("CSV file created: Rpackages_versions.csv")

```


