---
title: "mapping"
output: html_document
---

# Install and load packages:
```{r}
rm(list = ls())
pacman::p_load(
  tidyverse,
  ggplot2,
  here,
  stringr,
  paletteer,
  readr,
  dplyr,
  forcats,
  scales,
  treemapify,
  rphylopic,
  RColorBrewer,
  viridis,
  tidyr,
  forcats,
  bibliometrix,
  scales,
  treemap,
  ComplexUpset, # for upset plot
  patchwork,
  wordcloud2,
  textstem,
  SnowballC,
  sf,
  rnaturalearthdata,
  rnaturalearth,
  ggalluvial,
  circlize,
  countrycode,
  png
)


```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Load data
```{r}
#Load data
map <- read_csv(here("Data", "Dataset1_map_data_extraction.csv"))
biblio <- read_csv(here("Data", "Dataset2_bibliometric_data.csv"))
dat_policy <- read.csv(here("Data", "Dataset_3_policy_data_extraction.csv"))
pol_ci <- read_csv(here("Data", "Dataset_3.1_policy_citation_counts_PlumX.csv"))
dat_ceesat <- read.csv(here("Data", "Dataset5_ceesat_processed.csv"))
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 1: Systematic-map evidence matrix

## Setup and shared helpers

```{r figure-1-setup}
n_syntheses <- n_distinct(map$study_id)

# Restrained complementary palette inspired by editorial data graphics.
colours <- c(
  ink = "#243746",
  muted_ink = "#52636F",
  navy = "#315F7D",
  coral = "#B5687A",
  teal = "#568589",
  plum = "#74627D",
  moss = "#6E7F5B",
  slate = "#8A8F98",
  pale_navy = "#DCE7ED",
  pale_tile = "#EDF2F5",
  paper = "#FBFAF8",
  line = "#CBD3D8"
)

split_categories <- function(data, variable) {
  data %>%
    select(study_id, {{ variable }}) %>%
    separate_rows({{ variable }}, sep = ",") %>%
    mutate({{ variable }} := str_trim({{ variable }})) %>%
    filter(!is.na({{ variable }}), {{ variable }} != "") %>%
    distinct()
}

# Label helper: "Transportation (37)".
with_total <- function(label, n) paste0(label, " (", n, ")")


base_size <- 12

theme_map <- function() {
  theme_minimal(base_size = base_size) +
    theme(
      plot.background = element_rect(fill = colours["paper"], colour = NA),
      panel.background = element_rect(fill = colours["paper"], colour = NA),
      panel.grid = element_blank(),
      plot.title = element_text(
        face = "bold", size = base_size + 1, colour = colours["ink"],
        margin = margin(b = 10)
      ),
      plot.tag = element_text(
        face = "bold", size = base_size + 6, colour = colours["ink"]
      ),
      plot.tag.position = c(0, 1),
      axis.text = element_text(colour = colours["ink"], size = base_size - 0.5),
      axis.title = element_text(colour = colours["muted_ink"], size = base_size - 1),
      legend.text = element_text(colour = colours["muted_ink"], size = base_size - 1.5),
      legend.title = element_text(colour = colours["muted_ink"], size = base_size - 1.5),
      plot.margin = margin(10, 12, 10, 12)
    )
}
```
## Panel A: Publication year and synthesis approach

```{r figure-1-panel-a}
approach_by_year <- map %>%
  transmute(
    study_id,
    year,
    approach = if_else(
      str_to_lower(str_trim(quantitative)) == "yes",
      "Quantitative",
      "Narrative/Descriptive"
    )
  ) %>%
  distinct() %>%
  count(year, approach, name = "n") %>%
  complete(
    year = seq(min(map$year, na.rm = TRUE), max(map$year, na.rm = TRUE)),
    approach = c("Narrative/Descriptive", "Quantitative"),
    fill = list(n = 0)
  )

approach_counts <- approach_by_year %>%
  summarise(n = sum(n), .by = approach)

approach_labels <- set_names(
  with_total(approach_counts$approach, approach_counts$n),
  approach_counts$approach
)

year_totals <- approach_by_year %>%
  summarise(n = sum(n), .by = year) %>%
  filter(n > 0)

panel_a <- ggplot(approach_by_year, aes(x = year, y = n, fill = approach)) +
  geom_col(width = 0.62) +
  geom_text(
    data = year_totals,
    aes(x = year, y = n, label = n),
    inherit.aes = FALSE,
    vjust = -0.6,
    size = base_size / .pt * 0.92,
    colour = colours["muted_ink"]
  ) +
  scale_fill_manual(
    values = c(
      "Narrative/Descriptive" = unname(colours["coral"]),
      "Quantitative" = unname(colours["navy"])
    ),
    labels = approach_labels,
    name = NULL
  ) +
  scale_x_continuous(
    breaks = seq(min(approach_by_year$year), max(approach_by_year$year), by = 1),
    expand = expansion(mult = 0.015)
  ) +
  scale_y_continuous(
    breaks = c(0, 5, 10),
    expand = expansion(mult = c(0, 0.22))
  ) +
  labs(tag = "A", title = "PUBLICATION YEAR AND SYNTHESIS APPROACH", y = "Syntheses", x = NULL) +
  theme_map() +
  theme(
    panel.grid.major.y = element_line(colour = colours["line"], linewidth = 0.3),
    legend.position = c(0.01, 1.06),
    legend.justification = c(0, 1),
    legend.direction = "horizontal",
    legend.key.size = unit(11, "pt"),
    plot.title = element_text(
      face = "bold", size = base_size + 1, colour = colours["ink"],
      margin = margin(b = 22)
    )
  )
```
## Panel B: Noise source × biological outcome evidence matrix

```{r figure-1-panel-b}
noise_long <- split_categories(map, noise_source)
outcome_long <- split_categories(map, outcome_category)

noise_totals <- noise_long %>%
  count(noise_source, name = "total") %>%
  arrange(desc(total))

outcome_totals <- outcome_long %>%
  count(outcome_category, name = "total") %>%
  arrange(desc(total))

crosstab <- noise_long %>%
  inner_join(outcome_long, by = "study_id", relationship = "many-to-many") %>%
  count(noise_source, outcome_category, name = "n") %>%
  complete(
    noise_source = noise_totals$noise_source,
    outcome_category = outcome_totals$outcome_category,
    fill = list(n = 0)
  ) %>%
  left_join(noise_totals, by = "noise_source") %>%
  left_join(outcome_totals, by = "outcome_category") %>%
  mutate(
    noise_label = factor(
      with_total(noise_source, total.x),
      levels = rev(with_total(noise_totals$noise_source, noise_totals$total))
    ),
    outcome_label = factor(
      with_total(outcome_category, total.y),
      levels = with_total(outcome_totals$outcome_category, outcome_totals$total)
    ),
    # White numerals only where the tile is dark enough to carry them.
    label_colour = if_else(n >= 13, "#FFFFFF", unname(colours["ink"])),
    label_colour = if_else(n == 0, unname(colours["line"]), label_colour)
  )

panel_b <- ggplot(crosstab, aes(x = outcome_label, y = noise_label, fill = n)) +
  geom_tile(colour = colours["paper"], linewidth = 1.4) +
  geom_text(
    aes(label = n, colour = label_colour),
    size = base_size / .pt * 0.95
  ) +
  scale_colour_identity() +
  scale_fill_gradient(
    low = colours["pale_tile"],
    high = colours["ink"],
    name = "Syntheses per combination",
    guide = guide_colourbar(
      title.position = "left",
      title.vjust = 0.9,
      barwidth = unit(110, "pt"),
      barheight = unit(7, "pt"),
      ticks = FALSE
    )
  ) +
  scale_x_discrete(position = "top", expand = expansion(0)) +
  scale_y_discrete(expand = expansion(0)) +
  labs(tag = "B", title = "EVIDENCE MATRIX — NOISE SOURCE × BIOLOGICAL OUTCOME",
       x = NULL, y = NULL) +
  theme_map() +
  theme(
    axis.text.x.top = element_text(angle = 40, hjust = 0, vjust = 0,
                                   colour = colours["ink"]),
    legend.position = "bottom",
    legend.justification = "left",
    legend.direction = "horizontal",
    legend.margin = margin(t = 10)
  )
```
## Panel C: Taxonomic scope

```{r figure-1-panel-c}
vertebrate_taxa <- c("Aves", "Mammalia", "Reptilia", "Fish", "Amphibia")
invertebrate_taxa <- c(
  "Invertebrates", "Arthropoda", "Mollusca", "Cnidaria",
  "Echinodermata", "Annelida", "Bryozoa"
)

taxonomic_membership <- map %>%
  select(study_id, scope_taxon) %>%
  separate_rows(scope_taxon, sep = ",") %>%
  mutate(
    scope_taxon = str_to_title(str_trim(scope_taxon)),
    group = case_when(
      scope_taxon %in% vertebrate_taxa ~ "Vertebrate",
      scope_taxon %in% invertebrate_taxa ~ "Invertebrate",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(group)) %>%
  distinct(study_id, group)

# "Mixed" is the overlap of the two groups, not a third exclusive group: those
# syntheses are also counted in the Vertebrate and Invertebrate bars.
taxonomic_overlap <- taxonomic_membership %>%
  count(study_id) %>%
  summarise(n = sum(n == 2)) %>%
  pull(n)

taxonomic_counts <- taxonomic_membership %>%
  count(group, name = "n") %>%
  bind_rows(tibble(group = "Mixed", n = taxonomic_overlap)) %>%
  mutate(group = factor(group, levels = c("Mixed", "Invertebrate", "Vertebrate")))

panel_c <- ggplot(taxonomic_counts, aes(x = n, y = group, fill = group)) +
  geom_col(width = 0.62) +
  geom_text(
    aes(label = n),
    hjust = -0.35,
    size = base_size / .pt * 0.95,
    colour = colours["ink"]
  ) +
  scale_fill_manual(
    values = c(
      "Vertebrate" = unname(colours["plum"]),
      "Invertebrate" = unname(colours["teal"]),
      "Mixed" = unname(colours["slate"])
    ),
    guide = "none"
  ) +
  scale_x_continuous(limits = c(0, n_syntheses), expand = expansion(mult = c(0, 0.02))) +
  scale_y_discrete(expand = expansion(add = 0.5)) +
  labs(tag = "C", title = "TAXONOMIC SCOPE", x = NULL, y = NULL) +
  theme_map() +
  theme(
    axis.text.x = element_blank(),
    plot.title = element_text(
      face = "bold", size = base_size + 1, colour = colours["ink"],
      margin = margin(b = 4)
    )
  )
```
## Panel D: Environmental scope

```{r figure-1-panel-d}
environment_counts <- split_categories(map, ecosystem_type) %>%
  count(ecosystem_type, name = "n") %>%
  arrange(n) %>%
  mutate(ecosystem_type = fct_inorder(ecosystem_type))

panel_d <- ggplot(environment_counts, aes(x = n, y = ecosystem_type, fill = ecosystem_type)) +
  geom_col(width = 0.62) +
  geom_text(
    aes(label = n),
    hjust = -0.35,
    size = base_size / .pt * 0.95,
    colour = colours["ink"]
  ) +
  scale_fill_manual(
    values = c(
      "Marine" = unname(colours["navy"]),
      "Terrestrial" = unname(colours["moss"]),
      "Freshwater" = unname(colours["teal"]),
      "Urban" = unname(colours["coral"])
    ),
    guide = "none"
  ) +
  scale_x_continuous(limits = c(0, n_syntheses), expand = expansion(mult = c(0, 0.02))) +
  scale_y_discrete(expand = expansion(add = 0.5)) +
  labs(tag = "D", title = "ENVIRONMENTAL SCOPE", x = NULL, y = NULL) +
  theme_map() +
  theme(
    axis.text.x = element_blank(),
    plot.title = element_text(
      face = "bold", size = base_size + 1, colour = colours["ink"],
      margin = margin(b = 4)
    )
  )
```
## Panel E: Coverage breadth

```{r figure-1-panel-e}
breadth_of <- function(long_data, variable, label) {
  long_data %>%
    count(study_id, name = "categories") %>%
    summarise(
      Multiple = sum(categories > 1),
      Single = sum(categories == 1),
      assignments = sum(categories)
    ) %>%
    mutate(dimension = label, mean_categories = assignments / n_syntheses)
}

breadth <- bind_rows(
  breadth_of(noise_long, noise_source, "Noise sources"),
  breadth_of(outcome_long, outcome_category, "Outcomes"),
  breadth_of(split_categories(map, ecosystem_type), ecosystem_type, "Environments"),
  breadth_of(taxonomic_membership, group, "Taxon groups")
) %>%
  mutate(dimension = fct_inorder(dimension) %>% fct_rev())

breadth_long <- breadth %>%
  pivot_longer(c(Multiple, Single), names_to = "breadth", values_to = "n") %>%
  mutate(breadth = factor(breadth, levels = c("Multiple", "Single")))

panel_e <- ggplot(breadth_long, aes(x = n, y = dimension, fill = breadth)) +
  geom_col(width = 0.6, position = position_stack(reverse = TRUE)) +
  geom_text(
    aes(label = n, colour = breadth),
    position = position_stack(vjust = 0.5, reverse = TRUE),
    size = base_size / .pt * 0.88
  ) +
  scale_fill_manual(
    values = c(
      "Multiple" = unname(colours["ink"]),
      "Single" = unname(colours["pale_navy"])
    ),
    labels = c("Multiple" = "Multiple categories", "Single" = "Single"),
    name = NULL
  ) +
  scale_colour_manual(
    values = c("Multiple" = "#FFFFFF", "Single" = unname(colours["muted_ink"])),
    guide = "none"
  ) +
  scale_x_continuous(
    limits = c(0, n_syntheses),
    expand = expansion(mult = c(0, 0.02))
  ) +
  labs(tag = "E", title = "COVERAGE BREADTH", x = NULL, y = NULL) +
  theme_map() +
  theme(
    axis.text.x = element_blank(),
    legend.position = c(0.01, 1.10),
    legend.justification = c(0, 1),
    legend.direction = "horizontal",
    legend.key.size = unit(11, "pt"),
    plot.title = element_text(
      face = "bold", size = base_size + 1, colour = colours["ink"],
      margin = margin(b = 20)
    )
  )
```
## Assemble and save Figure 1

```{r figure-1-assemble}
# The right-hand panels are nested as their own patchwork. Laying C, D and E out
# in the same grid as B would make patchwork align their plot areas to B's, and
# B's panel starts low because of its rotated column labels — which pushed the
# C bars far below their title.
right_column <- wrap_plots(
  panel_c, panel_d, panel_e,
  ncol = 1,
  heights = c(0.80, 1.00, 1.00)
) +
  plot_annotation(
    theme = theme(
      plot.background = element_rect(fill = colours["paper"], colour = NA),
      plot.margin = margin(0, 0, 0, 0)
    )
  )

# wrap_elements() seals the right column into a single grob. Without it patchwork
# aligns C's plot area to B's, and B's panel starts low because of its rotated
# column labels — which dropped the C bars well below their own title.
body <- wrap_plots(
  panel_b,
  wrap_elements(full = right_column),
  nrow = 1,
  widths = c(4, 3)
)

figure_1 <- wrap_plots(panel_a, body, ncol = 1, heights = c(0.85, 3.15)) +
  plot_annotation(
    theme = theme(
      plot.background = element_rect(fill = colours["paper"], colour = NA),
      plot.margin = margin(10, 10, 10, 10)
    )
  )

figure_1

# Preserve the minimum 12-point typography by exporting at the dimensions below.
ggsave(
  here("Figures", "raw", "Figure_1_systematic_map_evidence_matrix.pdf"),
  figure_1,
  width = 14,
  height = 11,
  units = "in"
)

ggsave(
  here("Figures", "raw", "Figure_1_systematic_map_evidence_matrix.png"),
  figure_1,
  width = 14,
  height = 11,
  units = "in",
  dpi = 300
)
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure 2: Taxonomic groups

## Panel A: Taxonomic distribution TREEMAP
```{r}
# Split and clean taxa
taxon_long4 <- map %>%
  separate_rows(scope_taxon, sep = ",") %>%
  mutate(
    scope_taxon = str_trim(scope_taxon),
    scope_taxon = str_to_title(scope_taxon)
  )

# Get unique study counts per taxon (no double-counting)
taxon_counts3 <- taxon_long4 %>%
  distinct(study_id, scope_taxon) %>%
  group_by(scope_taxon) %>%
  summarise(mentions = n(), .groups = "drop")

# Assign group and subgroup
 vertebrates <- c("Aves", "Mammalia", "Reptilia", "Fish", "Amphibia")

taxon_counts3 <- taxon_counts3 %>%
  mutate(
    group = if_else(scope_taxon %in% vertebrates, "Vertebrate", "Invertebrate"),
    subgroup = scope_taxon
  ) %>%
  filter(mentions > 0)

# Assign pastel green and pastel purple gradients
vertebrate_subgroups <- vertebrates
invertebrate_subgroups <- setdiff(unique(taxon_counts3$subgroup), vertebrates)

# Assign colours for each group: pastel green for vertebrates pastel purple for invertebrates
pal_vertebrate <- scales::colour_ramp(c("#BBA0CA", "#600047"))(seq(0,1,length.out=length(vertebrate_subgroups)))
pal_invertebrate <- scales::colour_ramp(c("#B1B695", "#53917E"))(seq(0,1,length.out=length(invertebrate_subgroups)))

# Count data
taxon_counts3 <- taxon_counts3 %>%
  mutate(
    fill_color = case_when(
      group == "Vertebrate" ~ pal_vertebrate[match(subgroup, vertebrate_subgroups)],
      group == "Invertebrate" ~ pal_invertebrate[match(subgroup, invertebrate_subgroups)]
    ),
    label = paste0(scope_taxon, "\n(", mentions, ")")
  )

# Plot treemap (no subgroup label, just colored borders)
figure_2 <- ggplot(taxon_counts3, aes(area = mentions, fill = fill_color, label = label, subgroup = group)) +
  geom_treemap(color = "white", size = 1.8) +
  geom_treemap_subgroup_border(color = "white", size = 3) +   # Group borders only!
  # No geom_treemap_subgroup_text()  # <--- This removes the big faded group labels—for refining in vector editor software
  geom_treemap_text(
    fontface = "bold", colour = "White",
    place = "bottomleft", grow = FALSE, reflow = TRUE, min.size = 6
  ) +
  scale_fill_identity() +
  theme(
    plot.title = element_text(face = "bold", size = 20, hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),
    legend.position = "none",
    panel.background = element_rect(fill = "white", colour = NA),
    plot.background = element_rect(fill = "white", colour = NA)
  )

# Show figure
figure_2

# Save Figure
#ggsave(here("Figures/raw", "Figure_2_taxonomic_scope.pdf"), width = 14, height = 10, dpi = 300)
#ggsave(here("Figures", "Figure_2_taxonomic_scope.png"), width = 14, height = 10, dpi = 300)


```




#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 3: Bibliometric analysis

## Setup and country-name cleaning

```{r figure-3-setup}
# Panel B's co-authorship network comes from bibliometrix, matching the original
# Overview_figures.Rmd analysis. Set to FALSE to derive the same network directly
# from the Scopus affiliation strings instead (see build_edges_direct() below);
# both routes return the same 25 countries and 98 country pairs.
# Use the cleaned Scopus affiliation strings directly. This is equivalent to the
# bibliometrix route but avoids a version-sensitive `bibtag` import failure.
USE_BIBLIOMETRIX <- FALSE


colours <- c(
  ink = "#243746",
  muted_ink = "#52636F",
  paper = "#FBFAF8",
  land = "#E3E6E4",
  border = "#FBFAF8",
  graticule = "#DBE2E6"
)

base_size <- 12


# Constituent countries of the UK, plus the spellings Scopus emits.
uk_parts <- c("england", "scotland", "wales", "northern ireland", "uk",
              "united kingdom", "united kingdom.")

clean_country <- function(x) {
  x <- str_trim(x)
  x <- str_remove(x, "\\.$")
  low <- str_to_lower(str_trim(x))
  case_when(
    low %in% uk_parts ~ "United Kingdom",
    low %in% c("usa", "united states", "united states of america") ~ "United States",
    low == "russian federation" ~ "Russia",
    low == "czech republic" ~ "Czechia",
    low == "viet nam" ~ "Vietnam",
    TRUE ~ x
  )
}

# Country sits in the last comma-separated slot of a Scopus affiliation string.
country_of <- function(affiliation) {
  map_chr(affiliation, ~ {
    parts <- str_split(.x, ",")[[1]]
    clean_country(parts[length(parts)])
  })
}
```
## Panel A: First-author affiliation countries

```{r figure-3-panel-a}
first_author_country <- biblio %>%
  mutate(
    first_affiliation = map_chr(
      authors_with_affiliations,
      ~ str_trim(str_split(.x, ";")[[1]][1])
    ),
    country = country_of(first_affiliation)
  ) %>%
  count(country, name = "n_first_authors")

n_records <- nrow(biblio)

world <- ne_countries(scale = "medium", returnclass = "sf") %>%
  filter(admin != "Antarctica")

# Natural Earth uses its own naming; align the few that differ from Scopus.
ne_lookup <- c(
  "United States of America" = "United States",
  "United Kingdom" = "United Kingdom"
)

world_first <- world %>%
  mutate(
    match_name = recode(admin, !!!ne_lookup)
  ) %>%
  left_join(first_author_country, by = c("match_name" = "country"))

# Equal Earth: equal-area, so country sizes are proportionally honest, and it
# keeps the rounded silhouette that reads better than a plate carree rectangle.
crs_equal_earth <- "EPSG:8857"

world_ee <- st_transform(world_first, crs_equal_earth)
graticule <- st_graticule(
  lat = seq(-60, 80, 20),
  lon = seq(-180, 180, 60)
) %>%
  st_transform(crs_equal_earth)

land_bbox <- st_bbox(world_ee)

panel_a <- ggplot() +
  geom_sf(data = graticule, colour = colours["graticule"], linewidth = 0.25) +
  geom_sf(
    data = world_ee,
    aes(fill = n_first_authors),
    colour = colours["border"],
    linewidth = 0.12
  ) +
  scale_fill_stepsn(
    colours = c("#EBD9E6", "#D3A8CB", "#B173A8", "#8A4A82", "#5F2C5B"),
    na.value = colours["land"],
    breaks = c(2, 4, 6, 8),
    limits = c(0, 10),
    name = "First-author records",
    guide = guide_colorsteps(
      title.position = "top",
      barwidth = unit(190, "pt"),
      barheight = unit(10, "pt"),
      show.limits = FALSE
    )
  ) +
  # Crop to the land extent: with Antarctica dropped, the full projection would
  # leave a wide empty band of southern ocean.
  coord_sf(
    crs = crs_equal_earth,
    xlim = land_bbox[c("xmin", "xmax")],
    ylim = land_bbox[c("ymin", "ymax")],
    expand = FALSE
  ) +
  labs(tag = "A") +
  theme_void(base_size = base_size) +
  theme(
    plot.background = element_rect(fill = colours["paper"], colour = NA),
    legend.position = "bottom",
    legend.margin = margin(t = 2, b = 2),
    legend.title = element_text(size = base_size - 0.5, colour = colours["muted_ink"]),
    legend.text = element_text(size = base_size - 1, colour = colours["muted_ink"]),
    plot.tag = element_text(face = "bold", size = base_size + 6, colour = colours["ink"]),
    plot.tag.position = c(0, 1),
    plot.margin = margin(6, 6, 2, 6)
  )
```
## Panel B: Country co-authorship chord diagram

```{r figure-3-panel-b}
# Every country credited on a record, one row per record x country.
record_countries <- biblio %>%
  mutate(record = row_number()) %>%
  select(record, affiliations) %>%
  separate_rows(affiliations, sep = ";") %>%
  filter(str_trim(affiliations) != "") %>%
  mutate(country = country_of(affiliations)) %>%
  distinct(record, country)

# Records per country drives which sectors are small enough to pool.
records_per_country <- count(record_countries, country, name = "n_records")

# --- Route 1: bibliometrix (the analysis used in Overview_figures.Rmd) --------
build_edges_bibliometrix <- function() {
  bib <- bibliometrix::convert2df(
    here("Data", "bibliometric.bib"),
    dbsource = "scopus",
    format = "bibtex"
  )
  bib <- bibliometrix::metaTagExtraction(bib, Field = "AU_CO", sep = ";")
  net <- bibliometrix::biblioNetwork(
    bib,
    analysis = "collaboration",
    network = "countries",
    sep = ";"
  )
  m <- as.matrix(net)
  diag(m) <- 0
  m[lower.tri(m)] <- 0
  # bibliometrix returns upper-case country names.
  dimnames(m) <- list(
    clean_country(str_to_title(rownames(m))),
    clean_country(str_to_title(colnames(m)))
  )
  as.data.frame(as.table(m)) %>%
    set_names(c("country.x", "country.y", "n")) %>%
    mutate(across(c(country.x, country.y), as.character)) %>%
    filter(n > 0, country.x != country.y)
}

# --- Route 2: direct from Scopus affiliation strings -------------------------
build_edges_direct <- function() {
  record_countries %>%
    inner_join(record_countries, by = "record", relationship = "many-to-many") %>%
    filter(country.x < country.y) %>%
    count(country.x, country.y, name = "n")
}

edges_raw <- if (USE_BIBLIOMETRIX) {
  build_edges_bibliometrix()
} else {
  build_edges_direct()
}

# Countries credited on a single record are pooled into one "Other" sector; the
# ring is otherwise dominated by hairline sectors carrying long labels.
other_countries <- records_per_country %>%
  filter(n_records == 1) %>%
  pull(country) %>%
  sort()

other_label <- paste0("Other (", length(other_countries), ")")

pool <- function(x) if_else(x %in% other_countries, other_label, x)

edges <- edges_raw %>%
  mutate(country.x = pool(country.x), country.y = pool(country.y)) %>%
  # Re-sort each pair alphabetically so pooled duplicates merge cleanly.
  mutate(
    a = pmin(country.x, country.y),
    b = pmax(country.x, country.y)
  ) %>%
  summarise(n = sum(n), .by = c(a, b)) %>%
  rename(country.x = a, country.y = b)

# Order sectors by total collaboration volume, with Other pinned to the end.
country_strength <- bind_rows(
  edges %>% select(country = country.x, n),
  edges %>% select(country = country.y, n)
) %>%
  summarise(strength = sum(n), .by = country) %>%
  arrange(country == other_label, desc(strength))

chord_order <- country_strength$country

# Shorter display labels keep the ring from being swamped by text.
display_label <- function(x) {
  recode(
    x,
    "United States" = "USA",
    "United Kingdom" = "UK",
    .default = x
  )
}

adjacency <- edges %>%
  rename(from = country.x, to = country.y) %>%
  filter(from %in% chord_order, to %in% chord_order)

# Palette: distinct hues for the high-volume sectors, muted for the long tail.
sector_colours <- setNames(
  colorRampPalette(
    c("#6C5FC7", "#91D3C5", "#5D5D5D", "#BCCF7F", "#A9C7E8", "#C49ACF",
      "#B28A85", "#7A8BD1", "#6BB6C9", "#D6A9A5", "#E8C1A8", "#9FBBB0")
  )(length(chord_order)),
  chord_order
)

draw_chord <- function() {
  circos.clear()
  circos.par(
    track.margin = c(0.005, 0.005),
    gap.degree = 2.2,
    start.degree = 90,
    points.overflow.warning = FALSE,
    # Room for the outer labels so long names are not clipped.
    canvas.xlim = c(-1.16, 1.16),
    canvas.ylim = c(-1.16, 1.16)
  )
  chordDiagram(
    adjacency,
    order = chord_order,
    grid.col = sector_colours,
    transparency = 0.28,
    annotationTrack = "grid",
    annotationTrackHeight = mm_h(4),
    preAllocateTracks = list(track.height = 0.17),
    directional = 0,
    link.sort = TRUE,
    link.decreasing = TRUE
  )
  circos.trackPlotRegion(
    track.index = 1,
    bg.border = NA,
    panel.fun = function(x, y) {
      xlim <- get.cell.meta.data("xlim")
      sector <- get.cell.meta.data("sector.index")
      # Radial labels match the author-approved chord diagram.
      circos.text(
        mean(xlim), 0.86, display_label(sector),
        facing = "clockwise",
        niceFacing = TRUE,
        adj = c(0, 0.5),
        cex = 1.28,
        col = "#243746"
      )
    }
  )
  circos.clear()
}

# Capture the base-graphics chord as a high-resolution raster grob. This keeps
# the ring circular in patchwork without an additional conversion package.
chord_png <- tempfile(fileext = ".png")
grDevices::png(chord_png, width = 3000, height = 3000, res = 300, bg = colours["paper"])
draw_chord()
grDevices::dev.off()

chord_grob <- grid::rasterGrob(png::readPNG(chord_png), interpolate = TRUE)
unlink(chord_png)

panel_b <- patchwork::wrap_elements(full = chord_grob, clip = FALSE) +
  labs(tag = "B") +
  theme(
    plot.background = element_rect(fill = colours["paper"], colour = NA),
    plot.tag = element_text(face = "bold", size = base_size + 6, colour = colours["ink"]),
    plot.tag.position = c(0, 1),
    plot.margin = margin(-12, 6, 2, 6)
  )
```
## Assemble and save Figure 3

```{r figure-3-assemble}
figure_3 <- panel_a / panel_b +
  plot_layout(heights = c(0.50, 1)) +
  plot_annotation(
    theme = theme(
      plot.background = element_rect(fill = colours["paper"], colour = NA),
      plot.margin = margin(8, 8, 8, 8)
    )
  )

ggsave(
  here("Figures", "raw", "Figure_3_bibliometric_map_chord.pdf"),
  figure_3,
  width = 10,
  height = 15,
  units = "in"
)

ggsave(
  here("Figures", "raw", "Figure_3_bibliometric_map_chord.png"),
  figure_3,
  width = 10,
  height = 15,
  units = "in",
  dpi = 300
)

message("network source: ", if (USE_BIBLIOMETRIX) "bibliometrix" else "direct",
        " | records: ", n_records,
        " | first-author countries: ", nrow(first_author_country),
        " | chord sectors: ", length(chord_order),
        " | edges: ", nrow(adjacency))

# For the figure caption: name the countries pooled into the Other sector.
message("\n", other_label, " comprises: ",
        paste(other_countries, collapse = ", "), ".")

figure_3
```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 4: Policy analysis, alluvial plot top 10

```{r}
# Call data
dat <- dat_policy |>
  select(policy_topic, ecological_context, policy_document_type)

# Count combinations
dat_alluvial <- dat |>
  group_by(policy_topic, ecological_context, policy_document_type) |>
  summarise(Freq = n(), .groups = "drop")

# ---- Keep only top 5 most common flows ----
top5_flows <- dat_alluvial |>
  arrange(desc(Freq)) |>
  slice_head(n = 10)

dat_alluvial2 <- dat_alluvial |>
  semi_join(top5_flows,
            by = c("policy_topic", "ecological_context", "policy_document_type")) |>
  mutate(
    policy_topic        = fct_reorder(as.factor(policy_topic), Freq, .fun = sum, .desc = TRUE),
    ecological_context  = fct_reorder(as.factor(ecological_context), Freq, .fun = sum, .desc = TRUE),
    policy_document_type = fct_reorder(as.factor(policy_document_type), Freq, .fun = sum, .desc = TRUE)
  )

# Add line breaks in long labels
dat_alluvial2 <- dat_alluvial2 |>
  mutate(
    policy_document_type = fct_recode(policy_document_type,
      "Government\npolicy"       = "Government policy",
      "Regulatory\nSubmission"   = "Regulatory Submission",
      "Intergovernmental\npolicy" = "Intergovernmental policy"
    )
  )

# Colour palette
unicorn_pastel <- c(
  "Government\npolicy"        = "#D9BDE2",
  "Regulatory\nSubmission"    = "#BEECE0",
  "Intergovernmental\npolicy" = "#FFB5AA"
)
# Plot
figure_4 <- ggplot(dat_alluvial2,
                       aes(axis1 = policy_document_type,
                           axis2 = ecological_context,
                           axis3 = policy_topic,
                           y = Freq)
) +
  # Reorder axes: Document type → Ecological context → Policy topic
  scale_x_discrete(
    limits = c("policy_document_type", "ecological_context", "policy_topic"),
    labels = c("Document type", "Ecological context", "Policy topic"),
    position = "top",
    expand = c(.05, .05)
  ) +
  geom_alluvium(aes(fill = policy_document_type),
                width = 1/12, alpha = 0.6) +
  geom_stratum(aes(fill = after_stat(stratum)), color = "white", linewidth = 1.2) +
  geom_text(stat = "stratum",
            aes(label = after_stat(stratum)),
            size = 4) +
  scale_fill_manual(values = unicorn_pastel, na.value = "#f0f0f0") +
  theme_minimal(base_size = 14) +
  labs(y = NULL, x = NULL) +
  theme(
    legend.position = "none", # remove legend
    # Axis text
    axis.title.y = element_blank(),
    axis.text.y  = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x.top = element_text(face = "bold", size = 13, margin = margin(b = 10)),

    # Panel and grid tweaks
    panel.grid = element_blank(),   # remove gridlines
    panel.border = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA),

    # Overall text and title
    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, colour = "grey30"),
    plot.caption = element_text(size = 10, colour = "grey40", hjust = 1),

    # Strata labels spacing
    plot.margin = margin(10, 10, 10, 10)
  )

figure_4
#ggsave(here("Figures/raw", "Figure_4_scope_policy_documents_citing_syntheses.pdf"), width = 12, height = 9, dpi = 300)
#ggsave(here("Figures", "Figure_4_scope_policy_documents_citing_syntheses.png"), width = 12, height = 9, dpi = 300)




```



#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure 5: CEESAT scores: CEESAT question scores (all syntheses)

```{r}
# Labels:
labels <- structure(list(q = c("1.1", "2.1", "3.1", "3.2", "4.1", "4.2",
"4.3", "5.1", "5.2", "6.1", "6.2", "6.3", "7.1", "7.2", "7.3",
"8.1"), label = c("1.1 Research question and criteria",
"2.1 A priori protocol", "3.1 Systematic search approach",
"3.2 Search comprehensiveness", "4.1 Defined eligibility criteria",
"4.2 Consistent eligibility criteria",
"4.3 Reported eligibility decisions", "5.1 Critical appraisal",
"5.2 Critical appraisal cross-check",
"6.1 Data extraction method", "6.2 Data availability?",
"6.3 Data extraction cross-check",
"7.1 Choice of synthesis approach", "7.2 Appropiate meta-analysis",
"7.3 Variability investigation",
"8.1 Synthesis limitations"
)), row.names = c(NA, -16L), class = c("tbl_df", "tbl", "data.frame"
))
labels


# Filter and select relevant columns
ceesat_long <- dat_ceesat %>%
  select(starts_with("CEESAT")) %>%
  # Convert columns with "N/A" text to numeric, which creates proper NA values
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>%
  mutate(percent = n / sum(n) * 100)

# Prepare the data for plotting. Here, we join the calculated data with the labels and set up the 'value'
# column as a factor to control the order and appearance in the plot.
ceesat_for_plot <- ceesat_long %>%
  # Create a temporary column 'q' by removing "CEESAT" from the item name
  mutate(q = str_remove(item, "CEESAT")) %>%
  # Join with the labels data frame to get descriptive labels for the plot
  left_join(labels, by = "q") %>%
  # Prepare the 'value' column for plotting
  mutate(
    value = as.character(value),
    # Replace R's NA with a string "NA" for plotting
    value = ifelse(is.na(value), "NA", value),
    # Convert 'value' to a factor to control the stacking order in the legend and bars
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )

# Plot
figure_5 <- ggplot(ceesat_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5), # Center numbers on each bar segment
    size = 5,
    color = "black"
  ) +
  coord_flip() +
  scale_fill_manual(
    name = "Score",
    values = c(
      "0" = "#C73C55",
      "1" = "#DBA053",
      "3" = "#7CA982",
      "4" = "#E6D267"
    ),
    labels = c(
      "NA" = "N/A",
      "0" = "Red",
      "1" = "Amber",
      "3" = "Green",
      "4" = "Gold"
    )
  ) +
  labs(
    x = NULL, # The y-axis labels are self-explanatory
    y = "Percentage",
    fill = "Score"
  ) +
  labs(x = "CEESAT question", y = "Percentage", fill = NULL) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",        # remove legend
    panel.grid.major = element_blank(),  # remove major grid lines
    panel.grid.minor = element_blank(),  # remove minor grid lines
    axis.ticks = element_blank(),        # remove ticks
    axis.line = element_blank(),          # remove axis lines
    #increase font axis y
    axis.title.y = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    axis.text.y = element_text(size = 12), # Increase font size of question labels
    axis.text.x = element_text(size = 12)  # Increase font size of percentage labels
     )



figure_5
ggsave(here("Figures/raw", "Figure_5_CEESAT_assessment_syntheses.pdf"), width = 15, height = 9, dpi = 300)
ggsave(here("Figures", "Figure_5_CEESAT_assessment_syntheses.png"), width = 15, height = 9, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Syntheses quality analysis— Cited vs not cited in policy

```{r}
# Filter by meta-analysis
dat <- dat_ceesat %>%
  filter(!is.na(raw_score)) %>%
  mutate(
    max_possible_score = if_else(
      study_type_title_abstract == "Meta-analysis",
      64,
      56
    ),
    proportional_score = raw_score / max_possible_score
  )

# Confirm policy groups and check values
table(dat$cited_in_policy, useNA = "ifany")
summary(dat$proportional_score)
any(dat$proportional_score <= 0)

# Examine the distribution
hist(
  log(dat$proportional_score),
  main = "Log-transformed proportional CEESAT scores",
  xlab = "Log proportional score"
)

# Welch two-sample t-test
main_analysis <- t.test(
  log(proportional_score) ~ cited_in_policy,
  data = dat
)

main_analysis
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Supplementary figures
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S3: Synthesis characteristics and content mapping

## Panel A: Review type by publication year

```{r figure-s3-panel-a}
review_type_counts <- map %>%
  select(study_id, year, review_type) %>%
  distinct() %>%
  count(year, review_type, name = "paper_count") %>%
  complete(
    year = seq(min(map$year, na.rm = TRUE), max(map$year, na.rm = TRUE)),
    review_type = c("Systematic review", "Meta-analysis", "Systematic map"),
    fill = list(paper_count = 0)
  ) %>%
  mutate(
    review_type = factor(
      review_type,
      levels = c("Systematic review", "Meta-analysis", "Systematic map")
    )
  )

figS3_a <- ggplot(
  review_type_counts,
  aes(x = year, y = paper_count, fill = review_type)
) +
  geom_col(width = 0.7) +
  geom_text(
    data = filter(review_type_counts, paper_count > 0),
    aes(label = paper_count),
    position = position_stack(vjust = 0.5),
    size = 4,
    fontface = "bold"
  ) +
  scale_fill_manual(
    name = NULL,
    values = c(
      "Systematic review" = "#C6C1F0FF",
      "Meta-analysis" = "#F498B6FF",
      "Systematic map" = "#70C1BFFF"
    )
  ) +
  scale_x_continuous(
    breaks = seq(min(review_type_counts$year), max(review_type_counts$year), 1)
  ) +
  scale_y_continuous(limits = c(0, 12), breaks = seq(0, 12, 2)) +
  labs(x = NULL, y = "Number of syntheses", tag = "A") +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(0.18, 0.78),
    panel.grid = element_blank()
  )

figS3_a
```

## Panel B: Environment average per paper

```{r figure-s3-panel-b}
# Average number of environment types per paper
# sum(env_counts$paper_count)/50
# 1.56

# 1. Process ecosystem categories
env <- map %>%
  select(study_id, ecosystem_type) %>%
  mutate(ecosystem_type = str_split(ecosystem_type, ",\\s*")) %>%
  unnest(ecosystem_type) %>%
  mutate(ecosystem_type = str_trim(ecosystem_type)) %>%
  filter(!is.na(ecosystem_type), ecosystem_type != "") %>%
  distinct(study_id, ecosystem_type)

# 2. Count syntheses per ecosystem category
env_counts <- env %>%
  count(ecosystem_type, name = "paper_count") %>%
  arrange(-paper_count) %>%
  mutate(ecosystem_type = fct_reorder(ecosystem_type, paper_count))

# 3. Calculate automatic label
n_syntheses <- n_distinct(map$study_id)
env_total_assignments <- sum(env_counts$paper_count)
env_mean_categories <- env_total_assignments / n_syntheses

env_label <- paste0(
  "Mean ecosystem categories per synthesis:\n",
  sprintf("%.2f", env_mean_categories),
  " (", env_total_assignments,
  " category assignments\nacross ",
  n_syntheses,
  " syntheses)"
)

# 4. Show summary statistics
env_counts %>%
  mutate(percentage = (paper_count / n_syntheses) * 100) %>%
  print(n = Inf)

# 5. UpSet plot data
dat_upset_env <- env |>
  mutate(value = 1) |>
  pivot_wider(
    id_cols = study_id,
    names_from = ecosystem_type,
    values_from = value,
    values_fill = 0
  )

# 6. Plotting
figS3_b <- upset(
  dat_upset_env,
  intersect = colnames(dat_upset_env)[-1],
  name = "",
  base_annotations = list(
    "Intersection size" = intersection_size(
      mapping = aes(fill = 'bars_color')
    ) +
      annotate(
        geom = "text", x = Inf, y = Inf,
        label = env_label,
        vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'),
        guide = 'none'
      ) +
      scale_y_continuous(
        limits = c(0, 20),
        breaks = seq(0, 20, 4)
      ) +
      labs(tag = "B") +
      theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank()
      )
  ),
  matrix = intersection_matrix(
    geom = geom_point(shape = 16, size = 1.8)
  ),
  set_sizes = FALSE,
  min_size = 0
)

figS3_b

```


## Panel C: Noise source average per paper

```{r figure-s3-panel-c}
# Average number of noise sources per paper
# sum(noise_counts$paper_count)/50
# 2.84

# 1. Process noise-source categories
noise <- map %>%
  select(study_id, noise_source) %>%
  mutate(noise_source = str_split(noise_source, ",\\s*")) %>%
  unnest(noise_source) %>%
  mutate(noise_source = str_trim(noise_source)) %>%
  filter(!is.na(noise_source), noise_source != "") %>%
  distinct(study_id, noise_source)

# 2. Count syntheses per noise-source category
noise_counts <- noise %>%
  count(noise_source, name = "paper_count") %>%
  arrange(-paper_count) %>%
  mutate(noise_source = fct_reorder(noise_source, paper_count))

# 3. Calculate automatic label
n_syntheses <- n_distinct(map$study_id)

noise_total_assignments <- sum(noise_counts$paper_count)
noise_mean_categories <- noise_total_assignments / n_syntheses

noise_label <- paste0(
  "Mean noise-source categories per synthesis:\n",
  sprintf("%.2f", noise_mean_categories),
  " (", noise_total_assignments,
  " category assignments\nacross ",
  n_syntheses,
  " syntheses)"
)

# 4. Show summary statistics
noise_counts %>%
  mutate(percentage = (paper_count / n_syntheses) * 100) %>%
  print(n = Inf)

# 5. UpSet plot data
dat_upset_noise <- noise |>
  mutate(value = 1) |>
  pivot_wider(
    id_cols = study_id,
    names_from = noise_source,
    values_from = value,
    values_fill = 0
  )

# 6. Plotting
figS3_c <- upset(
  dat_upset_noise,
  intersect = colnames(dat_upset_noise)[-1],
  name = "",
  base_annotations = list(
    "Intersection size" = intersection_size(
      mapping = aes(fill = 'bars_color')
    ) +
      annotate(
        geom = "text", x = Inf, y = Inf,
        label = noise_label,
        vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'),
        guide = 'none'
      ) +
      scale_y_continuous(
        limits = c(0, 8),
        breaks = seq(0, 8, 2)
      ) +
      labs(tag = "C") +
      theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank()
      )
  ),
  matrix = intersection_matrix(
    geom = geom_point(shape = 16, size = 1.8)
  ),
  set_sizes = FALSE,
  min_size = 0
)

figS3_c

```
## Panel D. Outcome average per paper:

```{r figure-s3-panel-d}
# Average number of outcome categories per paper
# sum(outcome_counts$paper_count)/50
# 2.78

# 1. Process outcome categories
outcomes <- map %>%
  select(study_id, outcome_category) %>%
  mutate(outcome_category = str_split(outcome_category, ",\\s*")) %>%
  unnest(outcome_category) %>%
  mutate(outcome_category = str_trim(outcome_category)) %>%
  filter(!is.na(outcome_category), outcome_category != "") %>%
  distinct(study_id, outcome_category)

# 2. Count syntheses per outcome category
outcome_counts <- outcomes %>%
  count(outcome_category, name = "paper_count") %>%
  arrange(-paper_count) %>%
  mutate(outcome_category = fct_reorder(outcome_category, paper_count))

# 3. Calculate automatic label
n_syntheses <- n_distinct(map$study_id)

outcome_total_assignments <- sum(outcome_counts$paper_count)
outcome_mean_categories <- outcome_total_assignments / n_syntheses

outcome_label <- paste0(
  "Mean outcome categories per synthesis:\n",
  sprintf("%.2f", outcome_mean_categories),
  " (", outcome_total_assignments,
  " category assignments\nacross ",
  n_syntheses,
  " syntheses)"
)

# 4. Show summary statistics
outcome_counts %>%
  mutate(percentage = (paper_count / n_syntheses) * 100) %>%
  print(n = Inf)

# 5. UpSet plot data
dat_upset_outcomes <- outcomes |>
  mutate(value = 1) |>
  pivot_wider(
    id_cols = study_id,
    names_from = outcome_category,
    values_from = value,
    values_fill = 0
  )

# 6. Plotting
figS3_d <- upset(
  dat_upset_outcomes,
  intersect = colnames(dat_upset_outcomes)[-1],
  name = "",

  base_annotations = list(
    "Intersection size" = intersection_size(
      mapping = aes(fill = 'bars_color')
    ) +
      annotate(
        geom = "text", x = Inf, y = Inf,
        label = outcome_label,
        vjust = 1, hjust = 1
      ) +
      ylab("Number of syntheses") +
      scale_fill_manual(
        values = c('bars_color' = '#7370b3'),
        guide = 'none'
      ) +
      scale_y_continuous(
        limits = c(0, 10),
        breaks = seq(0, 10, 2)
      ) +
      labs(tag = "D") +
      theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank()
      )
  ),

  matrix = intersection_matrix(
    geom = geom_point(shape = 16, size = 1.8)
  ),

  set_sizes = FALSE,
  min_size = 0
)

figS3_d

```

## Patchwork plots—Figure S3
```{r figure-s3-assemble}
# Create panel pairs for better layout

figS3_ab <- (figS3_a | figS3_b) +
  plot_layout(nrow = 1) &
  theme(plot.tag = element_text(size = 14, face = "bold"))

figS3_cd <- (figS3_c | figS3_d) +
  plot_layout(nrow = 1) &
  theme(plot.tag = element_text(size = 14, face = "bold"))


# Create figure
figure_s3 <- figS3_ab / figS3_cd +
  plot_layout(nrow = 2) &
  theme(plot.tag = element_text(size = 14, face = "bold"))


# Save figure with all panels
figure_s3
ggsave(here("Figures/raw", "figure_s3.pdf"), figure_s3, width = 15, height = 10, dpi = 300)
ggsave(here("Figures/raw", "figure_s3.png"), figure_s3, width = 15, height = 10, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬


# Figure S4: Keywords
## Panel A: keyword bargraph
```{r}
# ---- Parameters ----
# Split by semi colon and then calculate frequency
dt.long <- biblio %>%
  select(author_keywords, index_keywords, doi) %>%
  pivot_longer(cols = c("author_keywords", "index_keywords")) %>%
  separate_longer_delim(col = "value",
                        delim = ";")
dt.long

#---------Create a synonnym diccionary -----------
synonyms <- c(
  # Meta-analysis variants
  "Meta Analysis"     = "Meta-Analysis",
  "Meta Analyses"     = "Meta-Analysis",
  "Literature Review" = "Review",

  # Fish variants
  "Fishes"            = "Fish",
  "Fishing"            = "Fishery",
  "Fish Physiology" = "Fish",
  "Fish Behaviour"    = "Fish",
  "Fishery"           = "Fishery",
  "Fisheries"           = "Fishery",
  "Pisces"            = "Fish",
  "Aquatic Organisms" = "Aquatic Species",
  "Aquatic Species" = "Aquatic Species",

  # Marine environment
  "Marine Soundscape" = "Marine",
  "Marine" = "Marine",
  "Marine Ecosystem" = "Marine Ecosystem",
  "Marine Ecosystems" = "Marine Ecosystem",
  "Marine Environment" = "Marine Ecosystem",
  "Marine Environments" = "Marine Ecosystem",
  "Marine vessels" = "Marine Vessel",
  "Marine vessel" = "Marine Vessel",
  "Vessel" = "Marine Vessel",
  "Vessels" = "Marine Vessel",
  "Ship" = "Marine Vessel",
  "Shipping" = "Marine Vessel",



  # Mammal variants
  "Mammals"           = "Mammal",
  "Mammalia"          = "Mammal",

  # Bird variants
  "Birds"             = "Bird",
  "Aves"              = "Bird",

  # Invertebrate variants
  "Invertebrates"     = "Invertebrate",
  "Invertebrata"      = "Invertebrate",

  # Animal variants
  "Animal"            = "Animals",
  "Fauna"            = "Animals",
  "Animalia"          = "Animals",
  "Wild Animal"       = "Wildlife",
  "Animals, Wild"     = "Wildlife",
  "Behavior, Animal"     = "Behaviour",
  "Behaviour, Animal"     = "Behaviour",
  "Behavioural"     = "Behaviour",
  "Behavior"  = "Behaviour",
  "Behavioral"  = "Behaviour",


  # Human variants
  "Humans"            = "Human",

  # Cetacean variants
  "Cetacea"           = "Cetaceans",
  "Cetacean"          = "Cetaceans",

  # Whale variants
  "Whales"            = "Whale",
  "Beluga Whales"     = "Beluga Whale",
  "Bowhead Whales"    = "Bowhead Whale",

  # Dolphin variants
  "Dolphins"          = "Dolphin",

  # Noise variants
  "Noise Impact"      = "Noise",
  "Noise-Induced Stress" = "Stress",

  # Anthropogenic noise variants
  "Anthrophony"       = "Anthropophony",
  "Anthropogenic Sounds" = "Anthropogenic Sound",
  "Anthropogenic Pollutants" = "Anthropogenic Pollutant",
  "Human-Induced Environmental Change" = "Human Disturbance",
  "Human Disturbances" = "Human Disturbance",
  "Human Disturbance" = "Human Disturbance",
  "Human Activities" = "Human Activity",
  "Human Activity" = "Human Activity",


  # Pollution variants
  "Sound Pollution"   = "Noise Pollution",
  "Acoustic Pollution"= "Noise Pollution",
  "Contaminación Por Ruido" = "Noise Pollution",
  "Contaminación Sonora"    = "Noise Pollution",
  "声污染"                 = "Noise Pollution",
  "噪音污染"                = "Noise Pollution",

  # Urbanization variants
  "Urbanización"      = "Urbanization",
  "城市化"              = "Urbanization",

  # Vertebrate variants
  "Vertebrates"       = "Vertebrate",
  "Vertebrata"        = "Vertebrate",

  # Review variants
  "Systematic Maps"   = "Systematic Map",
  "Systematic Literature Review" = "Systematic Review",
  "Scoping Review"    = "Scoping Review",
  "Review"            = "Review",

  # Risk variants
  "Risks Assessments" = "Risk Assessment",
  "Risk Evaluation"   = "Risk Assessment",
  # Environmental variants
  "Ecosystems" = "Ecosystem",
  "Ecosystem" = "Ecosystem",
  "Ecosystems" = "Ecosystem",
  "Environmental" = "Environment",
  "Environment" = "Environment",
  "Environmental Impacts" = "Environmental Impact",
  "Environmental Impact" = "Environmental Impact",
  "Environmental Disturbance" = "Environmental Impact",
  "Environmental Change" = "Environmental Impact",
  "Environmental Effect" = "Environmental Impact",
  "Environmental Fate" = "Environmental Impact",
  "Environmental Stressors" = "Environmental Stress",
  "Environmental Stress" = "Environmental Stress",
  "Environmental Impact Analysis" = "Environmental Impact Assessment",
  "Environmental Impacts Analysis" = "Environmental Impact Assessment",
  "Environmental Impact Assessments" = "Environmental Impact Assessment",
  "Environmental Policies" = "Environmental Policy",
  "Environmental Policy" = "Environmental Policy",
  "Conservation" = "Conservation",
  "Conservation Management" = "Conservation"

)

# ----Standardize case, trim whitespace ----
dt.long <- dt.long %>%
  mutate(value = str_to_title(value)) %>%
  mutate(value = trimws(value)) %>%
# Apply synonyms dictionary
  mutate(value = recode(value, !!!synonyms)) %>%
# drop NA
  filter(!is.na(value) & value != "")
# sort unique values
  sort(unique(dt.long$value))

# calculate number of mentions of each keyword—frequencies
keyword.freq <- dt.long %>%
  group_by(value) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

#-------Diagnostics-------
## number of mentions, including repeats
  nrow(dt.long)
## number of unique keywords after grouping
  nrow(keyword.freq)
## unique keyword count
  length(unique(dt.long$value))

## Find mising data
#setdiff(unique(dt.long$value), keyword.freq$value)

keyword.freq <- keyword.freq %>%
  arrange(-n)

# Clean NA
keyword.freq_clean <- keyword.freq %>%
  filter(!is.na(value))

# Reorder factor levels based on frequency for plotting
keyword.freq$value <- factor(keyword.freq$value,
                             levels = rev(keyword.freq$value))

# Plot
figS4_a <- ggplot(data = keyword.freq[1:20, ],
                    aes(x = n, y = value, fill = n))+
  geom_col()+
  scale_fill_gradient(low = "#B4D8E4", high = "#00425E")+
  xlab("Number of keywords")+
  ylab("Keyword")+
  #theme_bw()
  theme_minimal(base_size = 14) +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title.y = element_blank(),   # remove x axis title
        #axis.text.y  = element_blank(),   # remove x axis text
        axis.ticks.x = element_blank()
      )

figS4_a

#Save
#ggsave(here("Figures/raw", "Figure_S4A_keywords.pdf"), width = 12, height = 8, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S4A_keywords.png"), width = 12, height = 8, dpi = 300)

```
## Panel B - Cloud map

```{r}
# Extract a palette as a vector of hex colors
pal <- paletteer::paletteer_d("ggthemes::Purple_Pink_Gray")

# Convert to character (paletteer objects are special class)
pal <- as.character(pal)

# Word map
figS4_b <- wordcloud2(keyword.freq,
                      size = 1,
                      color = pal,
                      backgroundColor = "white",
                      shape = "rectangle"
)

# Show image-take a screenshot or export as png
figS4_b
```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S5: Academic citation count and the three most cited syntheses
```{r}
# 1. Create empty label column
biblio$label <- NA

# 2. Assign labels to the three top-cited papers
biblio$label[grepl("Benítez-López", biblio$authors) & biblio$year == 2010] <- "Benítez-López et al., 2010"
biblio$label[grepl("Shannon",       biblio$authors) & biblio$year == 2016] <- "Shannon et al., 2016"
biblio$label[grepl("Duarte",        biblio$authors) & biblio$year == 2021] <- "Duarte et al., 2021"

# 3. Make the citation scatterplot
figS5 <- ggplot(biblio, aes(x = year, y = cited_by)) +
  geom_jitter(size = 4.3, alpha = 0.25, color = "#8074A8FF", width = 0.3, height = 0) +
  geom_point(data = subset(biblio, !is.na(label)),
             aes(x = year, y = cited_by),
             color = "#8074A8FF", size = 4.3) +
  geom_label(data = subset(biblio, !is.na(label)),
             aes(label = label),
             hjust = -0.1, vjust = 0.4, size = 3.5,
             fill = "white", color = "black"
  ) +
   labs(
     x = NULL,
    y = "Academic citation count"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(biblio$year),
                                  to = max(biblio$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .75),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )



# 4. Print plot
figS5

#Save
#ggsave(here("Figures/raw", "Figure_S5_academic_citation_count.pdf"), width = 10, height = 7, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S5_academic_citation_count.png"), width = 16, height = 10, dpi= 300)


```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S6: Policy analysis, alluvial plot all variables

```{r}
# Alluvial plot with consistent pastel colors by Document Type ----
dat <- dat_policy |>
  select(policy_topic, ecological_context, policy_document_type)

dat_alluvial <- dat |>
  group_by(policy_topic, ecological_context, policy_document_type) |>
  summarise(Freq = n(), .groups = "drop")

# Prefix axis labels for uniqueness and reorder by frequency
dat_alluvial2 <- dat_alluvial |>
  mutate(
    policy_topic        = fct_reorder(as.factor(policy_topic), Freq, .fun = sum, .desc = TRUE),
    ecological_context  = fct_reorder(as.factor(ecological_context), Freq, .fun = sum, .desc = TRUE),
    policy_document_type = fct_reorder(as.factor(policy_document_type), Freq, .fun = sum, .desc = TRUE)
  ) |>
  # 🔑 Wrap long labels in Document type only
  mutate(
    policy_document_type = fct_relabel(policy_document_type, ~ str_replace_all(.x,
                                                                      c("Government policy"        = "Government\npolicy",
                                                                        "Regulatory Submission"    = "Regulatory\nSubmission",
                                                                        "Intergovernmental policy" = "Intergovernmental\npolicy")))
  )


# Unicorn pastel palette (keys must match new labels)
unicorn_pastel <- c(
  "Government\npolicy"        = "#D9BDE2",
  "Regulatory\nSubmission"    = "#BEECE0",
  "Intergovernmental\npolicy" = "#FFB5AA",
  "NGO report"                = "#B7D9EB",
  "Think Tank"                = "#D6D6F8",
  "Academic advisory"        = "#FFE3A3",
  "Other document"           = "#B6E06E"
)

# ---- Plot ----
figS6 <- ggplot(dat_alluvial2,
                       aes(axis1 = policy_document_type,
                           axis2 = ecological_context,
                           axis3 = policy_topic,
                           y = Freq)
) +
  scale_x_discrete(
    limits = c("policy_document_type", "ecological_context", "policy_topic"),
    labels = c("Document type", "Ecological context", "Policy topic"),
    position = "top",
    expand = c(.05, .05)
  ) +
 geom_alluvium(aes(fill = policy_document_type),
                width = 1/12, alpha = 0.8, knot.pos = 0.4) +
  geom_stratum(aes(fill = after_stat(stratum)),
               color = "white", linewidth = 1.2, width = 0.2) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 4) +
  scale_fill_manual(values = unicorn_pastel, na.value = "#f0f0f0") +

  theme_minimal(base_size = 14) +
  labs(y = "Count of papers", x = NULL) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.text.y  = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x.top = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA),
    plot.margin = margin(10, 10, 10, 10)
  )


figS6
#ggsave(here("Figures/raw", "Figure_S6_alluvialplot.pdf"), width = 10, height = 10, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S6_alluvialplot.png"), width = 10, height = 10, dpi = 300)

```



#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S7: Policy-citation counts by synthesis publication year
```{r}
# filter by policy cited or not
pol_fil <- pol_ci %>%
  filter(policy_cited == "Yes")

colnames(pol_fil)

# 3. Create empty label column
pol_cit <- pol_fil %>%
  mutate(label = case_when(
    study_id == "benitez_2010" ~ "Benítez-López et al., 2010",
    study_id == "shannon_2016" ~ "Shannon et al., 2016",
    TRUE ~ NA_character_
  ))



# 4. Make the citation scatterplot
figS7 <- ggplot(pol_cit, aes(x = year, y = unique_policy_citations)) +
  geom_jitter(size = 4.3, alpha = 0.25, color = "#8074A8FF", width = 0.3, height = 0) +
  geom_point(data = subset(pol_cit, !is.na(label)),
             aes(x = year, y = unique_policy_citations),
             color = "#8074A8FF", size = 4.3) +
  geom_label(data = subset(pol_cit, !is.na(label)),
             aes(label = label),
             hjust = -0.1, vjust = 0.4, size = 3.5,
             fill = "white", color = "black"
  ) +
   labs(
     x = NULL,
    y = "Policy documents citing syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(pol_cit$year),
                                  to = max(pol_cit$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .75),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )



# 5. Print plot
figS7

#Save
ggsave(here("Figures/raw", "Figure_S7_policyciting.pdf"), width = 10, height = 7, dpi = 300)
ggsave(here("Figures/raw", "Figure_S7_policyciting.png"), width = 10, height = 7, dpi = 300)
```
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S8: Policy trends

## Panel A: Policy topic trends

```{r}
# Step 1: Process outcomes
policytopic <- dat_policy %>%
  filter(!is.na(policy_document_type)) %>%
  #separate_rows(policy_topic, sep = ",\\s*") %>%
  mutate(policytopic = str_trim(policy_topic)) %>%
  filter(policy_topic != "") %>%
  distinct(study_id, policy_year, policy_topic) %>%
  count(policy_year, policy_topic, name = "n")

# Step 3: Plot (horizontal stacked bar with legend circles)
figS8_a <- ggplot(policytopic, aes(
  x = policy_year,,
  y    = n,
  fill = policy_topic
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy topic trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"
  ) +
  scale_x_continuous(breaks = seq(from = min(policytopic$policy_year),
                                  to = max(policytopic$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )
figS8_a

```


## Panel B: Policy ecological context trends

```{r}
# Step 1: Read data and process outcomes
# df <- read_csv(here("Data", "policy.csv"))

policy_eco <- dat_policy %>%
  filter(!is.na(ecological_context)) %>%
  #separate_rows(ecological_context, sep = ",\\s*") %>%
  mutate(ecological_context = str_trim(ecological_context)) %>%
  filter(ecological_context != "") %>%
  distinct(study_id, policy_year, ecological_context) %>%
  count(policy_year, ecological_context, name = "n")

# Step 3: Plot (horizontal stacked bar with legend circles)
figS8_b <- ggplot(policy_eco, aes(
  x    = policy_year,
  y    = n,
  fill = ecological_context
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy ecosystem trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(policy_eco$policy_year),
                                  to = max(policy_eco$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )

figS8_b
```
## Panel C: Policy document type trends

```{r}
# Manage data
policytype <- dat_policy %>%
  filter(!is.na(policy_document_type)) %>%
  #separate_rows(policy_document_type, sep = ",\\s*") %>%
  mutate(policy_document_typet = str_trim(policy_document_type)) %>%
  filter(policy_document_type != "") %>%
  distinct(study_id, policy_year, policy_document_type) %>%
  count(policy_year, policy_document_type, name = "n")



# Step 3: Plot (horizontal stacked bar with legend circles)
figS8_c <- ggplot(policytype, aes(
  x    = policy_year,
  y    = n,
  fill = policy_document_type
)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Policy document type trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Policy documents citing syntheses"
  ) +
  scale_x_continuous(breaks = seq(from = min(policytype$policy_year),
                                  to = max(policytype$policy_year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )

figS8_c
```

## Assemble Figure S8
```{r}
# Combine the panels to create the figure
figS8 <- figS8_a + figS8_b + figS8_c + plot_layout(nrow = 3) + plot_annotation(tag_levels = "A")

#Show figure
figS8

# Save figure
ggsave(here("Figures/raw", "Figure_S8_trends.pdf"), width = 11, height = 12, dpi = 300)
ggsave(here("Figures/raw", "Figure_S8_trends.png"), width = 11, height = 12, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S9: Annual trends cited and not cited in policy: Panel A, B and C: Syntheses cited and not cited in policy - stacked bar plots

## Overall annual-trend diagnostics supporting Figure S9

### Panel A: Outcome per time

```{r}
# Process outcomes
outcome_trends <- map %>%
  filter(!is.na(outcome_category)) %>%
  separate_rows(outcome_category, sep = ",\\s*") %>%
  mutate(outcome_category = str_trim(outcome_category)) %>%
  filter(outcome_category != "") %>%
  distinct(study_id, year, outcome_category) %>%
  count(year, outcome_category, name = "n")


# Plot (horizontal stacked bar with legend circles)
figS9_overall_a <- ggplot(outcome_trends, aes(
  x    = year,
  y    = n,
  fill = outcome_category
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = n),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Outcomes trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(outcome_trends$year),
                                  to = max(outcome_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )

#Show plot
figS9_overall_a
```


### Panel B: Noise source

```{r}
# Prepare data
noise_trends <- map %>%
  filter(!is.na(noise_source)) %>%
  separate_rows(noise_source, sep = ",") %>%
  mutate(noise_source = str_trim(noise_source)) %>%
  filter(noise_source != "") %>%
  distinct(study_id, year, noise_source) %>%
  count(year, noise_source, name = "count")

# Plot (horizontal stacked bar graoph with legend)
figS9_overall_b <- ggplot(noise_trends, aes(
  x    = year,
  y    = count,
  fill = noise_source
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = count),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
  scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Noise source",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
   labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(noise_trends$year),
                                  to = max(noise_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )

# Show pot
figS9_overall_b
```


### Panel C: Environment

```{r}

# Prepare data
ecosystem_trends <- map %>%
  filter(!is.na(ecosystem_type)) %>%
  separate_rows(ecosystem_type, sep = "[,;]") %>%
  mutate(ecosystem_type = str_trim(ecosystem_type)) %>%
  filter(ecosystem_type != "") %>%
  distinct(study_id, year, ecosystem_type) %>%
  count(year, ecosystem_type, name = "count")


# Plot bargraph
figS9_overall_c <-ggplot(ecosystem_trends, aes(
  x    = year,
  y    = count,
  fill = ecosystem_type
)) +
  geom_col(width = 0.7, position = position_stack()) +
  geom_text(
    aes(label = count),
    position = position_stack(vjust = 0.5),
    size = 3,
    colour = "white",
    fontface = "bold"
  ) +
   scale_fill_paletteer_d(
  "ggthemes::Purple_Pink_Gray",
  name = "Environment trends",
  guide = guide_legend(
    override.aes = list(
      shape = 21,
      size = 4,
      color = NA
    )
  )
  ) +
  labs(
     x = NULL,
    y = "Number of syntheses"#,
  ) +
  scale_x_continuous(breaks = seq(from = min(ecosystem_trends$year),
                                  to = max(ecosystem_trends$year), by = 1)
                     )+
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "inside",
    legend.position.inside = c(.15, .65),
    legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()

  )

# Show plot
figS9_overall_c

```

### Assemble the overall annual-trend diagnostic

```{r}
# We assembled the panels to create the final figure
figS9_overall <- figS9_overall_a + figS9_overall_b + figS9_overall_c + plot_layout(nrow = 3) + plot_annotation(tag_levels = "A")

# Show figure
figS9_overall

# Save figure
#ggsave(here("Figures/raw", "Figure_S9_overall_trends.pdf"), width = 11, height = 10, dpi = 300)
#ggsave(here("Figures/raw", "Figure_S9_overall_trends.png"), width = 11, height = 10, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬


```{r}
# Tidy data
tidy_trends <- map %>%
  select(study_id, year, cited_policy, outcome_category, noise_source, ecosystem_type) %>%
  pivot_longer(
    cols = c(outcome_category, noise_source, ecosystem_type),
    names_to = "category_group",
    values_to = "category_value"
  ) %>%
  filter(!is.na(category_value), category_value != "") %>%
  separate_rows(category_value, sep = "[,;]\\s*") %>%
  mutate(category_value = str_trim(category_value)) %>%

# Filter out "NA" values as requested
  filter(category_value != "NA") %>%
 # Selecting columns to plot
  group_by(year, cited_policy, category_group, category_value) %>%
  summarise(n = n_distinct(study_id), .groups = "drop")

# Creating a plotting function
create_trend_plot <- function(df, legend_title, plot_title = NULL) {

  ggplot(df, aes(x = year, y = n, fill = category_value)) +
    geom_col(width = 0.8, position = position_stack()) +

    # Count for each segment inside the bar
    geom_text(
      aes(label = n),
      position = position_stack(vjust = 0.5),
      size = 5,
      colour = "white",
      fontface = "bold"
    ) +

    scale_fill_paletteer_d("ggthemes::Purple_Pink_Gray", name = legend_title) +
    scale_x_continuous(
      breaks = seq(2008, 2025, 1),
      limits = c(2008, 2025)
    ) +
    scale_y_continuous(
      limits = c(0, 30),
      breaks = seq(0, 30, 5)
  )+
    labs(
      title = plot_title, # Title will be applied only if provided
      x = NULL,
      y = "Number of syntheses"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 16),
      legend.title = element_blank (),
      legend.text = element_text(size = 12),
      plot.title = element_text(face = "bold", size = 16, hjust = 0.5), # Larger title
      legend.position ="inside", legend.position.inside = c(.15, .65),
      axis.title.y = element_text(size = 18),
      axis.text.y = element_text(size = 18),
      axis.title.x = element_text(size = 18)
    )
}


```

## Panel A: Outcome category

```{r}
# Create individual plots for each combination of category_group and cited_policy, adjust theme individually

# Outcome category cited and not cited in policy
p_A <- tidy_trends %>%
  filter(category_group == "outcome_category", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Outcome", plot_title = "Not Cited in Policy") +
  labs(tag = "A") +
  theme (plot.tag = element_text(size = 20))


p_B <- tidy_trends %>%
  filter(category_group == "outcome_category", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Outcome", plot_title = "Cited in Policy") +
  theme(legend.position = "none",
        axis.title.y = element_blank())

# See plots
p_A
p_B

```

## Panel B: Noise source

```{r}
# Noise source cited and not cited in policy
p_C <- tidy_trends %>%
  filter(category_group == "noise_source", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Noise Source") +
  labs(tag = "B") +
  theme (plot.tag = element_text(size = 20))


p_D <- tidy_trends %>%
  filter(category_group == "noise_source", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Noise Source") +
   theme(legend.position = "none",
        axis.title.y = element_blank())

# See plots
p_C
p_D
```

## Panel C: Ecosystem type

``` {r}
# Ecosystem type cited and not cited in policy
p_E <- tidy_trends %>%
  filter(category_group == "ecosystem_type", cited_policy == "no") %>%
  create_trend_plot(legend_title = "Environment")+
  labs(tag = "C") +
  theme(axis.title.x = element_text(size = 18),
        plot.tag = element_text(size = 20))


p_F <- tidy_trends %>%
  filter(category_group == "ecosystem_type", cited_policy == "yes") %>%
  create_trend_plot(legend_title = "Environment") +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 18))

# See plots
p_E
p_F

```


## Patchwork Figure S9: Assemble the final figure

```{r}
# Assembling sub-figures in pairs for better alignment

figS9_a <- (p_A + p_B) +
  plot_layout(ncol = 2)

figS9_b <- (p_C + p_D) +
  plot_layout(ncol = 2)

figS9_c <- (p_E + p_F) +
  plot_layout(ncol = 2)

# Combining three rows for final figure

figS9 <- (figS9_a / figS9_b / figS9_c)

# Show final figure
figS9

# To save the figure
ggsave(here("Figures/raw", "Figure_S9_trends_syntheses_cited_not_cited.pdf"), width = 18, height = 15, dpi = 300)
ggsave(here("Figures/raw", "Figure_S9_trends_syntheses_cited_not_cited.png"), width = 18, height = 15, dpi = 300)

```

#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Figure S10: Geographical distribution of policy

## Panel A: Geographical distribution policy map
```{r}
policy_counts <- dat_policy %>%
  mutate(policy_country_clean = case_when(
    policy_country %in% c("Northern Ireland", "Scotland", "United Kingdom") ~ "United Kingdom",
    policy_country %in% c("USA", "U.S.A.", "United States") ~ "United States of America",
    TRUE ~ policy_country
  )) %>%
  filter(policy_country_clean != "International") %>%
  count(policy_country_clean, name = "n", sort = TRUE)

# Get the base count for the EU
eu_base_count <- policy_counts %>%
  filter(policy_country_clean == "European Union") %>%
  pull(n)

# Get the counts for individual countries
country_specific_counts <- policy_counts %>%
  filter(policy_country_clean != "European Union")
# ----------------------------------------------------
# CREATE FINAL COUNTS
# ----------------------------------------------------
world <- ne_countries(scale = "medium", returnclass = "sf")

map_data <- world %>%
  left_join(country_specific_counts, by = c("name" = "policy_country_clean")) %>%
  mutate(is_eu = !is.na(countrycode(name, "country.name", "eu28"))) %>%
  mutate(n_final = case_when(
    # For EU countries that ALSO have their own policies (e.g., Germany), ADD the counts.
    is_eu & !is.na(n) ~ n + eu_base_count,
    # For EU countries with NO specific policies, use the base EU count.
    is_eu & is.na(n)  ~ eu_base_count,
    # For non-EU countries, just use their own count.
    !is_eu            ~ n,
    # A fallback for any other case
    TRUE              ~ n
  ))

# PLOT THE MAP
figS10_a <- ggplot(data = map_data) +
  geom_sf(aes(fill = n_final), color = NA) +
  scale_fill_paletteer_c("ggthemes::Purple",
                         na.value = "#D8D8D8FF",
                         labels = number_format(accuracy = 1)) +
  labs(
    fill = "Combined policy count", # <-- Updated label for clarity
    caption = "EU countries are shown with a base count of 24, plus any country-specific counts."
  ) +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.caption = element_text(hjust = 0.5, size = 8, margin = margin(t = 5)) # Style the caption
  ) +
  guides(fill = guide_colorbar(
    title.position = "top",
    barwidth = 15,
    barheight = 0.5
  ))

# Show figure
figS10_a

# Save
ggsave(here("Figures/raw", "Figure_S10a_map_policy_countries.pdf"), width = 16, height = 14)
ggsave(here("Figures/raw", "Figure_S10a_map_policy_countries.png"), width = 16, height = 14, dpi = 300)
```



## Panel B: Top 10 policy document countries
```{r}
# Clean policy_country
dat_policy <- dat_policy %>%
  mutate(policy_country = case_when(
    policy_country %in% c("Northern Ireland", "Scotland", "United Kingdom") ~ "United Kingdom",
    TRUE ~ policy_country
  ))

# Clean and count countries
policy_country <- dat_policy %>%
  filter(!is.na(policy_country)) %>%
  mutate(policy_country = str_trim(policy_country)) %>%
  filter(policy_country != "") %>%
  #distinct(study_id, year, policy_country) %>%
  count(policy_country, name = "count")

# top 10
policy_country_top10 <- policy_country %>%
  slice_max(count, n = 10)

# Plot
figS10_b <- ggplot(policy_country_top10,
       aes(x = reorder(policy_country, count),
           y = count,
           fill = policy_country)
       ) +
    geom_col(fill = "#8074A8FF", width = 0.9) +
    geom_text(aes(label = count),
              hjust = 1.2, colour = "white", size = 5
              ) +
    labs(
        #title = "Policy document countries",
        x = NULL,
        y = "Policy documents count"
    ) +
   theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
    legend.position = "inside",
    #legend.position.inside = c(.15, .65),
    #legend.text = element_text(size = 9),
    legend.title = element_blank(),
    panel.grid = element_blank()
  )+
  coord_flip()

# Show figure
figS10_b

# Save figure
ggsave(here("Figures/raw", "Figure_S10b_toppol_countries.pdf"), width = 11, height = 8, dpi= 300)
ggsave(here("Figures/raw", "Figure_S10b_toppol_countries.png"), width = 11, height = 8, dpi = 300)
```

## Patchwork - Figure S10
```{r}
# Combine panels
figS10 <- figS10_a + figS10_b + plot_layout(nrow = 2) + plot_annotation(tag_levels = "A")

# Show figure
figS10

# Save figure
ggsave(here("Figures/raw", "Figure_S10_geographical_dist_policy.pdf"), width = 11, height = 8, dpi= 300)
ggsave(here("Figures/raw", "Figure_S10_geographical_dist_policy.png"), width = 11, height = 8, dpi = 300)
```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬

# Figure S11: CEESAT scores cited and not cited in policy

## Panel A: CEESAT scores (syntheses cited in policy):

```{r}
# 1. Labels
labels <- structure(list(q = c("1.1", "2.1", "3.1", "3.2", "4.1", "4.2",
"4.3", "5.1", "5.2", "6.1", "6.2", "6.3", "7.1", "7.2", "7.3",
"8.1"), label = c("1.1 Research question and criteria",
"2.1 A priori protocol", "3.1 Systematic search approach",
"3.2 Search comprehensiveness", "4.1 Defined eligibility criteria",
"4.2 Consistent eligibility criteria",
"4.3 Reported eligibility decisions", "5.1 Critical appraisal",
"5.2 Critical appraisal cross-check",
"6.1 Data extraction method", "6.2 Data availability?",
"6.3 Data extraction cross-check",
"7.1 Choice of synthesis approach", "7.2 Appropiate meta-analysis",
"7.3 Variability investigation",
"8.1 Synthesis limitations"
)), row.names = c(NA, -16L), class = c("tbl_df", "tbl", "data.frame"
))


# 2. Prepare the data for BOTH plots
# Data for CITED plot
ceesat_cited_for_plot <- dat_ceesat %>%
  filter(cited_in_policy == 1) %>%
  select(starts_with("CEESAT")) %>%
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>% summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>% mutate(percent = n / sum(n) * 100) %>%
  mutate(q = str_remove(item, "CEESAT")) %>%
  left_join(labels, by = "q") %>%
  mutate(
    value = as.character(value),
    value = ifelse(is.na(value), "NA", value),
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )

# Data for NOT CITED plot
ceesat_not_cited_for_plot <- dat_ceesat %>%
  filter(cited_in_policy == 0) %>%
  select(starts_with("CEESAT")) %>%
  mutate(across(c(CEESAT7.2, CEESAT7.3), ~suppressWarnings(as.numeric(.)))) %>%
  pivot_longer(cols = everything(), names_to = "item", values_to = "value") %>%
  group_by(item, value) %>% summarise(n = n(), .groups = "drop") %>%
  group_by(item) %>% mutate(percent = n / sum(n) * 100) %>%
  mutate(q = str_remove(item, "CEESAT")) %>%
  left_join(labels, by = "q") %>%
  mutate(
    value = as.character(value),
    value = ifelse(is.na(value), "NA", value),
    value = factor(value, levels = c("4", "3", "1", "0", "NA"))
  )


# 3. Create the individual plots with updated themes
common_theme <- theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 14) # Increase percentage label size for both plots
  )

# Plot A: Cited
figS11_a <- ggplot(ceesat_cited_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 5, color = "black") +
  coord_flip() +
  scale_fill_manual(name = "Score", values = c("0" = "#C73C55", "1" = "#DBA053", "3" = "#7CA982", "4" = "#E6D267"),
                    labels = c("0" = "Red", "1" = "Amber", "3" = "Green", "4" = "Gold")) +
  labs(x = NULL, y = NULL) +
  common_theme +
  # ---- THIS LINE INCREASES THE QUESTION FONT SIZE ----
  theme(axis.text.y = element_text(size = 14))

# Plot B: Not Cited
figS11_b <- ggplot(ceesat_not_cited_for_plot, aes(x = fct_rev(label), y = percent, fill = value)) +
  geom_col(width = 0.8) +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 5, color = "black") +
  coord_flip() +
  scale_fill_manual(name = "Score", values = c("0" = "#C73C55", "1" = "#DBA053", "3" = "#7CA982", "4" = "#E6D267"),
                    labels = c("NA" = "N/A", "0" = "Red", "1" = "Amber", "3" = "Green", "4" = "Gold")) +
  labs(x = NULL, y = NULL) +
  common_theme +
  theme(axis.text.y = element_blank())

#figS11_a
#figS11_b

```

## Patchwork- Figure S11 CEESAT

```{r}
# Combine panels to create figure
figS11 <- (figS11_a | figS11_b) +
  plot_annotation(
    tag_levels = 'A',
    caption = 'Percentage'
  ) &
  theme(
    legend.position = "none",
    plot.caption = element_text(hjust = 0.6, size = 14)
  )

# 5. Display the final combined plot
figS11
#ggsave(here("Figures/raw", "Figure_S11_CEESATcited_notcited.pdf"), width = 16, height = 9, dpi= 300)
#ggsave(here("Figures/raw", "Figure_S11_CEESATcited_notcited.png"), width = 16, height = 9, dpi = 300)

```


#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
#¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬¬
# Packages citations

```{r}
# List of packages
pkgs <- c(
  "tidyverse","ggplot2","here","stringr","paletteer","readr","dplyr","forcats",
  "scales","treemapify","rphylopic","RColorBrewer","viridis","tidyr","mapproj",
  "bibliometrix","viridisLite","treemap","ComplexUpset","patchwork","wordcloud2",
  "janitor","textstem","SnowballC","webshot","countrycode","sf","rnaturalearthdata",
  "rnaturalearth","ggrepel","packcircles","ggforce", "tidyverse", "sf"
)

# Function to safely get BibTeX citation
get_bib <- function(pkg) {
  tryCatch(
    toBibtex(citation(pkg)),
    error = function(e) paste0("% Error getting citation for: ", pkg, "\n")
  )
}

# Collect citations
bibs <- lapply(pkgs, get_bib)

# Flatten list into a single character vector
bibs_text <- unlist(bibs)

# Write to file
writeLines(bibs_text, "Rpackages_citations.bib")

message("Bib file created: Rpackages_citations.bib")

```
```{r}
# List of packages
pkgs <- c(
  "tidyverse","ggplot2","here","stringr","paletteer","readr","dplyr","forcats",
  "scales","treemapify","rphylopic","RColorBrewer","viridis","tidyr","mapproj",
  "bibliometrix","viridisLite","treemap","ComplexUpset","patchwork","wordcloud2",
  "janitor","textstem","SnowballC","webshot","countrycode","sf","rnaturalearthdata",
  "rnaturalearth","ggrepel","packcircles","ggforce", "sf"
)

# Get versions
pkg_versions <- sapply(pkgs, function(pkg) {
  tryCatch(as.character(packageVersion(pkg)), error = function(e) NA)
})

# Print neatly
print(pkg_versions)

# Optionally export to CSV
versions_df <- data.frame(
  Package = names(pkg_versions),
  Version = unname(pkg_versions),
  stringsAsFactors = FALSE
)

#write.csv(versions_df, "Rpackages_versions.csv", row.names = FALSE)

#message("CSV file created: Rpackages_versions.csv")

```
